### 2020-06-14 paper.tex
forex paper V.1, pushed by CH

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% As of May 2020, [sigchi] and [sigchi-a] are no longer used. Please use sigconf (above) for SIGCHI conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for conferences using one-column small layout
% \documentclass[acmsmall,review]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Forexast: A Interactive News Digestion for Forex Investors}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Trovato}
\authornote{Both authors contributed equally to this research.}
\email{trovato@corporation.com}
\orcid{1234-5678-9012}
\author{G.K.M. Tobin}
\authornotemark[1]
\email{webmaster@marysville-ohio.com}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}

\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Charles Palmer}
\affiliation{%
  \institution{Palmer Research Laboratories}
  \streetaddress{8600 Datapoint Drive}
  \city{San Antonio}
  \state{Texas}
  \postcode{78229}}
\email{cpalmer@prl.com}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Foreign exchange (forex) markets reflect real-world events, local or global.  Thus,  financial news is oftentimes referred to when making predicting the trends of forex. We propose News Forexast,  an interactive web-based system that displays a forex plot alongside with related financial news. Users can locate specific periods when the trading trends in forex markets dramatically change with the visualization of Standard Deviation (SD) events and Directional Change (DC) events. Finally, Forex comes with a keyword filtering function that allows users to filter news with keywords. We aim to make the decision-making process smoother for not only professional financial analysts but also all investors with this accessible and intuitive website.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10002951.10003260.10003282</concept_id>
       <concept_desc>Information systems~Web applications</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Web applications}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{forex, financial news, standard deviation, directional change}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{teaser.png}
  \caption{Forexast available at http://}
  \Description{}
  \label{fig:teaser}
\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
Foreign exchange (Forex) market has been one of the most popular market for decades, with an estimated \$1\  trillion traded every day\cite{YAO200079}. Spot trading, options future and exchange-traded funds(ETFs) are three of many ways of investing strategies adopted in forex markets\cite{TradeForex}. The strategies might vary but they are driven by an intuitive rule of thumb, which is to buy low and sell high\cite{KOOLEN2014144}\cite{Zervos11}. Therefore, whether investors can accurately forecast the prices or trends is extremely crucial. Forex markets are influenced by numerous factors, such as producer price index(PPI), interest rates and politics, in order to consider as many factors as possible to have more comprehensive approaches for forex investment, investors rely on news for them to stay informed. Besides the fact that news usually reflect the real world events, the similar nature of news and forex also makes these two co-dependent. For example, if the Federal Reserve System (Fed) cuts the interest rate, it is more likely that the value of USD would drop, the devaluation would then feed into forex market increasing the demand, thus making another piece of news.

\section{Related Work and Systems}
The dynamics between news and forex markets have been explored from several different aspects. Evans and Lyons proved that news can have significant effects on currency for days\cite{EVANS2005197}, and more specifically macro news can affect currency prices directly and indirectly via order flow\cite{EVANS200826}. There is also more evidence showcasing news and forex trend are correlated, Bauwens, Omrane and Giot show that volatility increases right before the announcement of scheduled news and unscheduled-but-periodic news\cite{BAUWENS20051108}, while Chatrath et al. suggests that prices respond quickly within 5-min of the news release\cite{CHATRATH201442}. With how forex markets and news interact in mind, it is only reasonable to suggest traders should begin their days by reading news commentary to determine the market sentiment and the daily direction for trading\cite{samuels2015trader}.

There are many trading websites which provide useful information for forex investors, and each of them has its own features\cite{ForexWebsites}. For instance, BabyPips\cite{BabyPips} is a friendly website for junior traders, which provides not only forex plots and data but also courses, tutorials and forums for beginners. Bloomberg\cite{Bloomberg} is a well-known news agency. Therefore, besides stocks and currencies data, it also has various categories of news. TradingView\cite{TradingView} provides numerous functions in a page, such as watchlist, alerts, headlines and real-time chats, where users can customize the settings. However, some of their news and forex plot are not put in the same interface, or the times of news and forex are not highlighted. This could neglect the relation between news and forex data. Therefore, our work aims to highlight the connection between the timing of news and forex trends. New Forexast is designed to display the news’ release time as vertical lines on the forex plot to emphasize the order of breaking news and exchange rates. In addition, when users hover on the line, the background colour of the corresponding news would change. 
We also choose to display standard deviation events (SD events) and directional change events (DC events)\cite{7850020} to help users locate the changes within exchange rates, and pay more attention to the changes of trend or where the prices have larger volatility. The features of News Forexast would be introduced more detailed in section 4.

\section{System Structure}

\subsection{Data Collection}
The forex data is from philipperemy/FX-1-Minute-Data\cite{FX-1-Minute-Data}, a repository of github. We choose the EUR/USD index, and use the DateTime Stamp, OPEN Bid Quote, HIGH Bid Quote, LOW Bid Quote and CLOSE Bid Quote columns as our forex data. The time span is from 2019/08/04 to 2019/09/13 except Saturdays, and the granularity of data is minute.

The news data is crawled by us, containing titles, sources, release times and urls. There are 1116 news in total and the sources are all from The Wall Street Journal\cite{WSJ}.

\subsection{Algorithms for DC and SC events}
To mark some special time points on the plot, we use two algorithms, standard deviation events (SD events) and directional change events (DC events)\cite{7850020}. SD events show the times where the prices dramatically change, and DC events show the times where the trends change. To get these events, we need to calculate the difference rate list $D$ of the price list first. 
Let $P= [p_1, p_2, ..., p_n]$, where $p_t$ stands for the CLOSE Bid Quote at minute $t$ and n equals to total numbers of daily forex data. Then we can get a difference rate list $D= [d_1, d_2, ..., d_m]$, where $d_t = \frac{p_{t+w}-p_t}{p_t}$.  $w\in\mathbb Z^+$ means the range in minutes, which can be freely customized (we use 30 in this demonstration).
$\sigma$ is the standard deviation of $D$, which can be interpreted as the volatility of prices. We use $\sigma$ as our low threshold to attain a subset of D, whose elements are all bigger than $\sigma$. Then the corresponding set of p will be marked as SD events. We also consider $2\sigma$ and $3\sigma$ as medium and high thresholds in our demonstration. Higher threshold will find less events.

Under the DC framework, the market is summarized into alternating uptrends and downtrends\cite{7850020}. A DC event, including a start point and an end point, can be seen as a period that the trend starts to change. At first, we do not know the prices start with a upward or downward trend, so we let the first element of price $p_1$ as a base. Then we start looking through the list until we find a current price $p_c$, where $|\frac{p_c-p_1}{p_1}| > \theta$, $\theta$ can be set to $\sigma$, $2\sigma$, $3\sigma$ as above mentioned. If $p_c > p_1$, that means the span from $p_1$ to $p_c$ is an upward DC event; otherwise, it is a downward DC event. After finding the first DC event, we still have to look through the rest. Let us consider a market starts with a downtrend, which means we are now in an downtrend and waiting for a next uptrend. We keep updating the lowest price $p_l$ in this downtrend until we find a current price $p_c$ that $\frac{p_c-p_l}{p_l} > \theta$. Then, we mark that the span from $p_l$ to $p_c$ is a upward DC event, and the trend become upward. Similarly, if a market is in a uptrend, we keep updating the highest price $p_h$ until we find a current $p_c$ that $\frac{p_h-p_c}{p_c} > \theta$, then $p_h$ to $p_c$ is a downward DC event, and the trend become downward. After finishing looking through all daily forex data, we can get a series of alternating DC events.

\section{Interfaces and features}
The interface of News Forexast can be divided into two main parts, a forex chart and the news section. Users can customize the selection criteria either by directly manipulating the forex chart or applying the keyword filters.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{hover.png}
  \caption{Example of news being highlighted when the cursor hovers over the corresponding timeline on the chart.}
  \Description{}
\end{figure}

\subsection{Interactive Forex Chart}
The forex chart is a standard candlestick chart, powered by Plotly graphing libraries\cite{Plotly}, that displays price movements, users can specify the date they are interested in with the calendar icon above the chart. Supported by Plotly graphing library, users can explore the chart freely by zooming in or dragging out the time frame they are interested. The corresponding news would be highlighted if users hover over the corresponding blue line on the chart. (Fig. 2)

Below the calendar is where users can specify event types and the corresponding thresholds. After selecting an event type and their thresholds, eg. SD and low threshold,  the algorithmic output would be shown on the forex chart. Once done with a specific setting, users can clear the setting with the “clear all” button the top-right. The news section without any specification would show all daily news with titles, released time and sources. Users could link to the original posts and websites by clicking on the news cards.

\subsection{Forex Event Identifier}
With the help of SD and DC events as indicators, users can now spot specific time ranges they are interested in. (Fig 3, 4) Users can then select such time range on the plot and narrow down the news shown on the right to the time range they selected. For example, users can specify 2019/08/30 with the SD with the low threshold, users can tell that there’s a dramatic change during 14:30-16:30 and can proceed to select the time range on the plot. In return, the news section would display related news such as "Would Warren Buffett Buy Greenland?" and "Risky Seller Financing Flourishes Where Homes Are Cheapest".

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sd.png}
  \caption{Examples of displaying SD events on 2019/08/30. The top is set to low threshold and the bottom is set to high threshold. Due to the higher sensitivity, almost all events of the latter are in the slump period around 16:00.}
  \Description{}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{dc.png}
  \caption{Examples of displaying DC events on 2019/08/30. The top is set to low threshold and the bottom is set to high threshold. Due to the higher sensitivity, the latter only summarize the daily market into a downtrend and an uptrend.}
  \Description{}
\end{figure}

\subsection{Customizable Keyword Filter
}
If interested in more specific news, users can use the button under the plot to filter out news with selected keywords. We have placed several keywords such as U.S. and Trump, users can also customize their own tags by clicking the “+” button. For example, if the time frame is specified and the tag "U.S" is applied, only "Strength in U.S. Consumer Spending Drives Economy". would be shown on the news section.(Fig 5)

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{news.png}
  \caption{Examples of filtering news on 2019/08/30. From left to right are none, keyword: 'U.S.', time: '14:30-16:30', and both.}
  \Description{}
\end{figure}

\section{Conclusion and Future work}
We have proposed an interactive website that juxtaposes a forex chart with news within the time frame users selecting. By having the chart and related news side by side together, users, financial professional or amateur investors, can all understand the trend quicker and easier. We are working toward to provide real-time news update in the future, as fixed data is limited. In addition, if we are able to collect more user's log data and news in the future, along with machine learning and natural language processing (NLP) techniques, we can achieve more customized news feed such as personal news recommendation.

\section{Acknowledgments}

\bibliographystyle{ACM-Reference-Format}
\bibliography{reference}

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

### 2020-06-17 paper.tex
Revise abstract, intro, related work -- cjwang.

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Forexast: A Interactive News Digestion for Forex Investors}
+\title{Forexast: An Interactive News Digestion for Forex Investors}
 
@@
 %% used to denote shared contribution to the research.
-\author{Ben Trovato}
-\authornote{Both authors contributed equally to this research.}
-\email{trovato@corporation.com}
-\orcid{1234-5678-9012}
-\author{G.K.M. Tobin}
-\authornotemark[1]
-\email{webmaster@marysville-ohio.com}
+
+\author{Chih-Hen Lee}
+\email{ch.lee@citi.sinica.edu.tw}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin}
-  \state{Ohio}
-  \postcode{43017-6221}
-}
+  \institution{Research Center for Information Technology Innovation, Academia Sinica}
+  \city{Taipei}
+  \country{Taiwan}}
 
-\author{Huifen Chan}
+\author{Yi-Shyuan Chiang}
+\email{yschiang@gapp.nthu.edu.tw}
 \affiliation{%
-  \institution{Tsinghua University}
-  \streetaddress{30 Shuangqing Rd}
-  \city{Haidian Qu}
-  \state{Beijing Shi}
-  \country{China}}
+  \institution{Research Center for Information Technology Innovation, Academia Sinica}
+  \city{Taipei}
+  \country{Taiwan}}
 
-\author{Charles Palmer}
+\author{Chuan-Ju Wang}
+\email{cjwang@citi.sinica.edu.tw}
 \affiliation{%
-  \institution{Palmer Research Laboratories}
-  \streetaddress{8600 Datapoint Drive}
-  \city{San Antonio}
-  \state{Texas}
-  \postcode{78229}}
-\email{cpalmer@prl.com}
+  \institution{Research Center for Information Technology Innovation, Academia Sinica}
+  \city{Taipei}
+  \country{Taiwan}}
 
@@
 \begin{abstract}
-Foreign exchange (forex) markets reflect real-world events, local or global.
-Thus,  financial news is oftentimes referred to when making predicting the trends of forex.
-We propose News Forexast,  an interactive web-based system that displays a forex plot alongside with related financial news.
-Users can locate specific periods when the trading trends in forex markets dramatically change with the visualization of Standard Deviation (SD) events and Directional Change (DC) events.
-Finally, Forex comes with a keyword filtering function that allows users to filter news with keywords.
-We aim to make the decision-making process smoother for not only professional financial analysts but also all investors with this accessible and intuitive website.
+Foreign exchange (Forex) markets reflect real-world events, locally or globally.
+Thus,  financial news is oftentimes leveraged for predicting the trends of forex.
+In this demonstration, we propose Forexast, an interactive web-based system that displays a forex plot alongside with related financial news.
+To our best knowledge, this is the first system that successfully aligns the presentation of two types of time-series data: the forex data and the textual news data in a unified and time-aware manner.
+Specifically, we first present two event detection methods based on the standard deviation (SD) and directional change (DC) of the forex data and use them to locate specific periods when the trends in forex markets dramatically change.
+Moreover, Forexast comes with a keyword filtering function that allows users to filter news with self-defined keywords.
+The system can be of great help in revealing valuable insights and relations between two types of time-series data and thus be valuable for decision making for not only professional financial analysts or traders but also common investors.
+The system is now online available at \url{http: //clip.csie.org/10K/}.
 \end{abstract}
@@
 \section{Introduction}
-Foreign exchange (Forex) market has been one of the most popular market for decades, with an estimated \$1\  trillion traded every day\cite{YAO200079}.
-Spot trading, options future and exchange-traded funds(ETFs) are three of many ways of investing strategies adopted in forex markets\cite{TradeForex}.
-The strategies might vary but they are driven by an intuitive rule of thumb, which is to buy low and sell high\cite{KOOLEN2014144}\cite{Zervos11}.
+Foreign exchange (Forex) market has been one of the most popular financial markets for decades, with an estimated \$1\ trillion traded every day~\cite{YAO200079}.
+Spot trading, currency options, currency futures, and currency exchange-traded funds (ETFs) are four major ways to trade Forex~\cite{TradeForex}.
+The strategies might vary but they are driven by an intuitive rule of thumb, which is to buy low and sell high~\cite{KOOLEN2014144,Zervos11}.
 Therefore, whether investors can accurately forecast the prices or trends is extremely crucial.
-Forex markets are influenced by numerous factors, such as producer price index(PPI), interest rates and politics, in order to consider as many factors as possible to have more comprehensive approaches for forex investment, investors rely on news for them to stay informed.
-Besides the fact that news usually reflect the real world events, the similar nature of news and forex also makes these two co-dependent.
-For example, if the Federal Reserve System (Fed) cuts the interest rate, it is more likely that the value of USD would drop, the devaluation would then feed into forex market increasing the demand, thus making another piece of news.
 
-\section{Related Work and Systems}
-The dynamics between news and forex markets have been explored from several different aspects.
-Evans and Lyons proved that news can have significant effects on currency for days\cite{EVANS2005197}, and more specifically macro news can affect currency prices directly and indirectly via order flow\cite{EVANS200826}.
-There is also more evidence showcasing news and forex trend are correlated, Bauwens, Omrane and Giot show that volatility increases right before the announcement of scheduled news and unscheduled-but-periodic news\cite{BAUWENS20051108}, while Chatrath et al.
-suggests that prices respond quickly within 5-min of the news release\cite{CHATRATH201442}.
-With how forex markets and news interact in mind, it is only reasonable to suggest traders should begin their days by reading news commentary to determine the market sentiment and the daily direction for trading\cite{samuels2015trader}.
+Forex markets are influenced by numerous factors, such as producer price index (PPI), interest rates, and politics.
+In order to consider as many factors as possible to have more comprehensive views for Forex investment, most investors rely on news for them to stay informed.
+Besides the fact that news usually reflect the real-world events, the similar nature of news and forex also makes these two co-dependent.
+For example, if the Federal Reserve System (Fed) cuts the interest rate, it is more likely that the value of USD would drop; also, such a devaluation would later make another piece of news~\cite{"CNBC"}.
 
-There are many trading websites which provide useful information for forex investors, and each of them has its own features\cite{ForexWebsites}.
-For instance, BabyPips\cite{BabyPips} is a friendly website for junior traders, which provides not only forex plots and data but also courses, tutorials and forums for beginners.
-Bloomberg\cite{Bloomberg} is a well-known news agency.
-Therefore, besides stocks and currencies data, it also has various categories of news.
-TradingView\cite{TradingView} provides numerous functions in a page, such as watchlist, alerts, headlines and real-time chats, where users can customize the settings.
-However, some of their news and forex plot are not put in the same interface, or the times of news and forex are not highlighted.
-This could neglect the relation between news and forex data.
-Therefore, our work aims to highlight the connection between the timing of news and forex trends.
-New Forexast is designed to display the news’ release time as vertical lines on the forex plot to emphasize the order of breaking news and exchange rates.
-In addition, when users hover on the line, the background colour of the corresponding news would change.
-We also choose to display standard deviation events (SD events) and directional change events (DC events)\cite{7850020} to help users locate the changes within exchange rates, and pay more attention to the changes of trend or where the prices have larger volatility.
-The features of News Forexast would be introduced more detailed in section 4.
+Considering the critical roles of news for Forex investment, in this demonstration, we propose Forexast, an interactive web-based system that displays a forex plot alongside with related financial news.
+The proposed system aims to highlight the connection between two types of time-series data: the Forex and the news data by aligning the timing of them.
+Forexast is designed to display the news' release time as vertical lines on the forex plot to emphasize the order of breaking news and exchange rates.
+In addition, when users hover on a vertical line, the background colour of the corresponding news would change.
+Moreover, we propose to use two event detection methods based on the standard deviation (SD) and directional change (DC)~\cite{7850020} of the Forex data to locate specific periods when the trends in Forex markets dramatically change.
+Via this design, user can pay more attention to the changes of trend or where the prices have larger volatility.
+Finally, Forexast comes with a keyword filtering function that allows users to filter news with self-defined keywords.
+To our best knowledge, this is the first system that effectively visualizes two types of time-series data: the forex data and the textual news data in a unified and time-aware manner. 
+The proposed Forexast can be of great help in revealing valuable insights and relations between two types of time-series data and thus be valuable for decision making for not only professional financial analysts or
 
-\section{System Structure}
+The remainder of this paper is organized as follows.
+In Section~\ref{sec:related}, we review previous studies related to Forex and news and major websites for Forex traders.
+Section~\ref{sec:system} describes the proposed system with details related to data collection, event detection algorithms, interfaces and key features.
+After that, we provide a case study in section~\ref{sec:case} and Section~\ref{sec:conclude} provides the conclusion and future work.
+
+\section{Related Work and Systems}\label{sec:related}
+The dynamics between news and Forex markets have been explored from several different aspects.
+Evans and Lyons (2005) prove that news can have significant effects on currency for days~\cite{EVANS2005197}, and macro news can affect currency prices directly and indirectly via order flow~\cite{EVANS200826}.
+There is also more evidence showcasing news and Forex trend are correlated.
+For instance, Bauwens et al.
+(2005) show that volatility increases right before the announcement of scheduled news and unscheduled-but-periodic news~\cite{BAUWENS20051108}, while Chatrath et al.
+(2014) suggest that prices respond quickly within 5-min after the news release~\cite{CHATRATH201442}.
+With how Forex markets and news interact in mind, it is reasonable for traders to begin their days by reading news commentary to determine the market sentiment and the direction for trading~\cite{samuels2015trader}.
+
+Apart from the literature discussing the relation between Forex and news, there are many trading websites which provide useful information for Forex investors, each of which has its own features and limitations~\cite{ForexWebsites}.
+For instance, BabyPips\footnote{\url{https://www.babypips.com}} is a friendly website for junior traders, providing not only Forex plots but also courses, tutorials and forums for beginners.
+Bloomberg\footnote{\url{https://www.bloomberg.com}} is a well-known news agency; thus, in addition to currency data and plots, it also provides various categories of news for users to focus on their interest.
+TradingView\footnote{\url{https://www.tradingview.com}} provides numerous functions in a page, such as watchlist, alerts, headlines and real-time chats, where users can customize the settings. 
+However, most of these websites do not put the news and Forex plot at the same page or do not explicitly align the news releasing time with the Forex prices.
+Most of them neglect the time-dependent relation between news and Forex data and thus do not effectively visualizes two types of time-series data: in a unified and time-aware manner.
+
+\section{System Description}\label{sec:system}
 
 \subsection{Data Collection}
-The forex data is from philipperemy/FX-1-Minute-Data\cite{FX-1-Minute-Data}, a repository of github.
+The forex data is from philipperemy/FX-1-Minute-Data\footnote{\url{https://github.com/philipperemy/FX-1-Minute-Data}}, a repository of github.
 We choose the EUR/USD index, and use the DateTime Stamp, OPEN Bid Quote, HIGH Bid Quote, LOW Bid Quote and CLOSE Bid Quote columns as our forex data.
@@
 
-The news data is crawled by us, containing titles, sources, release times and urls. There are 1116 news in total and the sources are all from The Wall Street Journal\cite{WSJ}.
+The news data is crawled by us, containing titles, sources, release times and urls.
+There are 1116 news in total and the sources are all from The Wall Street Journal\footnote{\url{https://www.wsj.com}}.
 
-\subsection{Algorithms for DC and SC events}
+\subsection{Algorithms for SD and DC events}
 To mark some special time points on the plot, we use two algorithms, standard deviation events (SD events) and directional change events (DC events)\cite{7850020}.
@@
 
-\section{Interfaces and features}
+\subsection{Interfaces and features}
 The interface of News Forexast can be divided into two main parts, a forex chart and the news section.
@@
   \includegraphics[width=\linewidth]{hover.png}
-  \caption{Example of news being highlighted when the cursor hovers over the corresponding timeline on the chart.}
+  \caption{Example of news being highlighted when the cursor hovers over the corresponding timeline on the chart. The yellow interval is the news selection range which can be decided by users.}
   \Description{}
@@
 
-\subsection{Interactive Forex Chart}
-The forex chart is a standard candlestick chart, powered by Plotly graphing libraries\cite{Plotly}, that displays price movements, users can specify the date they are interested in with the calendar icon above the chart.
+\subsubsection{Interactive Forex Chart}
+The forex chart is a standard candlestick chart, powered by Plotly graphing libraries\footnote{\url{https://https://plotly.com/graphing-libraries/}}, that displays price movements, users can specify the date they are interested in with the calendar icon above the chart.
 Supported by Plotly graphing library, users can explore the chart freely by zooming in or dragging out the time frame they are interested.
@@
 
-\subsection{Forex Event Identifier}
+\subsubsection{Forex Event Identifier}
 With the help of SD and DC events as indicators, users can now spot specific time ranges they are interested in.
@@
 
-\subsection{Customizable Keyword Filter
+\subsubsection{Customizable Keyword Filter
 }
@@
 
-\section{Conclusion and Future work}
-We have proposed an interactive website that juxtaposes a forex chart with news within the time frame users selecting.
+\section{Case Study}\label{sec:case}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{case.png}
+  \caption{An example of case study.}
+  \Description{}
+\end{figure}
+
+In this section, we provide an example that showcases the strong relation among events, news and forex (Fig 6).
+On 2019/08/06, we can see the news "Welcome to Turnaround Tuesday" released at 08:43, the time when an uptrend is about to end (displaying DC event with high threshold shows that this uptrend starts at 05:07).
+The news mentioned "U.S.
+stock futures were in a decidedly better mood as Tuesday began than on Monday." This indicates that U.S.
+stock is likely to rebound later, and thus causes appreciation on USD.
+Then, the EUR/USD starts a downtrend from 08:49 to 14:41.
+Note that if EUR/USD has lower rate, it could be explained that USD has relatively high value.
+
+\section{Conclusion and Future work}\label{sec:conclude}
+We have proposed an interactive website that juxtaposes a forex chart with news from the time frame users selecting.
 By having the chart and related news side by side together, users, financial professional or amateur investors, can all understand the trend quicker and easier.
-We are working toward to provide real-time news update in the future, as fixed data is limited.
+We are working toward to provide real-time news update in the future, as forex data is limited.
 In addition, if we are able to collect more user's log data and news in the future, along with machine learning and natural language processing (NLP) techniques, we can achieve more customized news feed such as personal news recommendation.

### 2020-06-20 paper.tex
Revise the whole paper -- cjwang.

@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Forexast: An Interactive News Digestion for Forex Investors}
+\title{INForex: An Interactive News Digestion for Forex Investors}
 
@@
 \author{Chih-Hen Lee}
+\authornote{Both authors contributed equally to this work.}
 \email{ch.lee@citi.sinica.edu.tw}
@@
 \author{Yi-Shyuan Chiang}
+\authornotemark[1]
 \email{yschiang@gapp.nthu.edu.tw}
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+\renewcommand{\shortauthors}{Lee, Chiang and Wang}
 
@@
 Foreign exchange (Forex) markets reflect real-world events, locally or globally.
-Thus,  financial news is oftentimes leveraged for predicting the trends of forex.
-In this demonstration, we propose Forexast, an interactive web-based system that displays a forex plot alongside with related financial news.
-To our best knowledge, this is the first system that successfully aligns the presentation of two types of time-series data: the forex data and the textual news data in a unified and time-aware manner.
-Specifically, we first present two event detection methods based on the standard deviation (SD) and directional change (DC) of the forex data and use them to locate specific periods when the trends in forex markets dramatically change.
-Moreover, Forexast comes with a keyword filtering function that allows users to filter news with self-defined keywords.
+Thus,  financial news is oftentimes leveraged for predicting the trends of Forex.
+In this demonstration, we propose INForex, an interactive web-based system that displays a Forex plot alongside with related financial news.
+To our best knowledge, this is the first system that successfully aligns the presentation of two types of time-series data: the Forex data and the textual news data in a unified and time-aware manner.
+Specifically, we first present two event detection methods based on the standard deviation (SD) and directional change (DC) of the Forex data and use them to locate specific periods when the prices or trends in Forex markets dramatically change.
+Moreover, INForex comes with a keyword filtering function that allows users to filter news with self-defined keywords.
 The system can be of great help in revealing valuable insights and relations between two types of time-series data and thus be valuable for decision making for not only professional financial analysts or traders but also common investors.
-The system is now online available at \url{http: //clip.csie.org/10K/}.
+The system is now online available at ~\url{http://chlee.pythonanywhere.com/forex/}.
 \end{abstract}
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{forex, financial news, standard deviation, directional change}
+\keywords{Forex, financial news, standard deviation, directional change}
 
@@
 \begin{teaserfigure}
-  \includegraphics[width=\textwidth]{teaser.png}
-  \caption{Forexast available at http://}
+  \includegraphics[width=\textwidth]{teaser.pdf}
+  \caption{INForex available at~\url{http://chlee.pythonanywhere.com/forex/}.}
   \Description{}
@@
 In order to consider as many factors as possible to have more comprehensive views for Forex investment, most investors rely on news for them to stay informed.
-Besides the fact that news usually reflect the real-world events, the similar nature of news and forex also makes these two co-dependent.
+Besides the fact that news usually reflect the real-world events, the similar nature of news and Forex also makes these two co-dependent.
 For example, if the Federal Reserve System (Fed) cuts the interest rate, it is more likely that the value of USD would drop; also, such a devaluation would later make another piece of news~\cite{"CNBC"}.
 
-Considering the critical roles of news for Forex investment, in this demonstration, we propose Forexast, an interactive web-based system that displays a forex plot alongside with related financial news.
+Considering the critical roles of news for Forex investment, in this demonstration, we propose INForex, an interactive web-based system that displays a Forex plot alongside with related financial news.
 The proposed system aims to highlight the connection between two types of time-series data: the Forex and the news data by aligning the timing of them.
-Forexast is designed to display the news' release time as vertical lines on the forex plot to emphasize the order of breaking news and exchange rates.
+INForex is designed to display the news' release time as vertical lines on the Forex plot to emphasize the order of breaking news and exchange rates.
 In addition, when users hover on a vertical line, the background colour of the corresponding news would change.
-Moreover, we propose to use two event detection methods based on the standard deviation (SD) and directional change (DC)~\cite{7850020} of the Forex data to locate specific periods when the trends in Forex markets dramatically change.
+Moreover, we propose to use two event detection methods based on the standard deviation (SD) and directional change (DC)~\cite{7850020} of the Forex data to locate specific periods when the prices or trends in Forex markets dramatically change.
 Via this design, user can pay more attention to the changes of trend or where the prices have larger volatility.
-Finally, Forexast comes with a keyword filtering function that allows users to filter news with self-defined keywords.
-To our best knowledge, this is the first system that effectively visualizes two types of time-series data: the forex data and the textual news data in a unified and time-aware manner. 
-The proposed Forexast can be of great help in revealing valuable insights and relations between two types of time-series data and thus be valuable for decision making for not only professional financial analysts or
+Finally, INForex comes with a keyword filtering function that allows users to filter news with self-defined keywords.
+To our best knowledge, this is the first system that effectively visualizes two types of time-series data: the Forex data and the textual news data in a unified and time-aware manner. 
+The proposed INForex can be of great help in revealing valuable insights and relations between two types of time-series data and thus be valuable for decision making for not only professional financial analysts or traders but also common investors.
 
@@
 However, most of these websites do not put the news and Forex plot at the same page or do not explicitly align the news releasing time with the Forex prices.
-Most of them neglect the time-dependent relation between news and Forex data and thus do not effectively visualizes two types of time-series data: in a unified and time-aware manner.
+Most of them neglect the time-dependent relation between news and Forex data and thus do not effectively visualizes two types of time-series data in a unified and time-aware manner.
 
@@
 \subsection{Data Collection}
-The forex data is from philipperemy/FX-1-Minute-Data\footnote{\url{https://github.com/philipperemy/FX-1-Minute-Data}}, a repository of github.
-We choose the EUR/USD index, and use the DateTime Stamp, OPEN Bid Quote, HIGH Bid Quote, LOW Bid Quote and CLOSE Bid Quote columns as our forex data.
-The time span is from 2019/08/04 to 2019/09/13 except Saturdays, and the granularity of data is minute.
+The Forex data was collected from philipperemy/FX-1-Minute-Data.\footnote{\url{https://github.com/philipperemy/FX-1-Minute-Data}}
+For demonstration purpose, we chose the EUR/USD index and used the DateTime Stamp, OPEN Bid Quote, HIGH Bid Quote, LOW Bid Quote and CLOSE Bid Quote columns to plot the Forex candlestick chart; moreover, the time span for the Forex data is from August 4, 2019 to September 13, 2019, and the granularity of data is minute.
+As for the news, we crawled the data from The Wall Street Journal,\footnote{\url{https://www.wsj.com}} each of which contains the title, the source, the release time, and the corresponding url.
+In this demonstration, there are 1,116 news in total.
 
-The news data is crawled by us, containing titles, sources, release times and urls.
-There are 1116 news in total and the sources are all from The Wall Street Journal\footnote{\url{https://www.wsj.com}}.
+\subsection{Event Detection Algorithms}\label{sec:algo}
+The proposed system comes with two event detection algorithms: one is based on the standard deviation of Forex price differences (referred as SD events hereafter) and one is based on the directional change of Forex prices (referred as DC events hereafter)~\cite{7850020}.
+Specifically, SD events indicate the time points where the Forex prices dramatically change, whereas DC events show the time points where the trends of Forex prices change.
 
-\subsection{Algorithms for SD and DC events}
-To mark some special time points on the plot, we use two algorithms, standard deviation events (SD events) and directional change events (DC events)\cite{7850020}.
-SD events show the times where the prices dramatically change, and DC events show the times where the trends change.
-To get these events, we need to calculate the difference rate list $D$ of the price list first.
-Let $P= [p_1, p_2, ..., p_n]$, where $p_t$ stands for the CLOSE Bid Quote at minute $t$ and n equals to total numbers of daily forex data.
-Then we can get a difference rate list $D= [d_1, d_2, ..., d_m]$, where $d_t = \frac{p_{t+w}-p_t}{p_t}$.
-$w\in\mathbb Z^+$ means the range in minutes, which can be freely customized (we use 30 in this demonstration).
-$\sigma$ is the standard deviation of $D$, which can be interpreted as the volatility of prices.
-We use $\sigma$ as our low threshold to attain a subset of D, whose elements are all bigger than $\sigma$.
-Then the corresponding set of p will be marked as SD events.
-We also consider $2\sigma$ and $3\sigma$ as medium and high thresholds in our demonstration.
-Higher threshold will find less events.
+We here briefly describe the two algorithms.
+Let $P= [p_1, p_2, ..., p_n]$ denote a series of Forex prices, where $p_t$ stands for the CLOSE Bid Quote at minute $t$ and $n$ equals to the total numbers of daily Forex data; also, the series of difference rates between two Forex prices is defined as $\mathcal{D}= [d_1, d_2, ..., d_m]$, where $d_t = {(p_{t+w}-p_t)}/{p_t}$ and $w\in\mathbb Z^+$ denotes the range in minutes.
+Note that we set $w=30$ in our prototype system.
+We first calculate the standard deviation of differences in list $\mathcal{D}$ and denoted it as $\sigma_\mathcal{D}$; we then use the $z$-score of each difference to determine the event events (i.e., $z_{d_i}=(|d_i-m_{\mathcal{D}}|)/\sigma_{\mathcal{D}}>\tau$) , where $m_{\mathcal{D}}$ denotes the mean of the list $\mathcal{D}$.)
+In this demonstration, we consider $\tau=1,2,3$ as our thresholds that correspond to the label \emph{Low}, \emph{Medium}, and \emph{High} in the system. 
+Note that a higher threshold locates less events.
 
-Under the DC framework, the market is summarized into alternating uptrends and downtrends\cite{7850020}.
+As for the DC events, the market is summarized into a set of uptrend and downtrend events~\cite{7850020}.
 A DC event, including a start point and an end point, can be seen as a period that the trend starts to change.
-At first, we do not know the prices start with a upward or downward trend, so we let the first element of price $p_1$ as a base.
-Then we start looking through the list until we find a current price $p_c$, where $|\frac{p_c-p_1}{p_1}| > \theta$, $\theta$ can be set to $\sigma$, $2\sigma$, $3\sigma$ as above mentioned.
-If $p_c > p_1$, that means the span from $p_1$ to $p_c$ is an upward DC event; otherwise, it is a downward DC event.
-After finding the first DC event, we still have to look through the rest.
-Let us consider a market starts with a downtrend, which means we are now in an downtrend and waiting for a next uptrend.
-We keep updating the lowest price $p_l$ in this downtrend until we find a current price $p_c$ that $\frac{p_c-p_l}{p_l} > \theta$.
-Then, we mark that the span from $p_l$ to $p_c$ is a upward DC event, and the trend become upward.
-Similarly, if a market is in a uptrend, we keep updating the highest price $p_h$ until we find a current $p_c$ that $\frac{p_h-p_c}{p_c} > \theta$, then $p_h$ to $p_c$ is a downward DC event, and the trend become downward.
-After finishing looking through all daily forex data, we can get a series of alternating DC events.
+At first, we let the first element in the price list $p_1$ as a starting point of the algorithm; then, the algorithm starts looking through the price list $P$ in a sequential manner until it locates a price $p_c$ that $|{(p_c-p_1)}/{p_1}|>\theta$.
+In this demonstration, we consider $\theta=\sigma_{\mathcal{D}},2\sigma_{\mathcal{D}},3\sigma_{\mathcal{D}}$ as our thresholds that as well as correspond to the label \emph{Low}, \emph{Medium}, and \emph{High} in the system.
+If $p_c > p_1$, the span from $p_1$ to $p_c$ denotes an upward DC event; otherwise, it is a downward DC event.
+After finding the first DC event, we start to locate other DC events in the rest of the price sequence.
+Let us consider a market starts with a downtrend, meaning that the Forex market is now in a downtrend and waiting for a next uptrend, for which we keep updating the lowest price $p_\ell$ in this downtrend until we find a price $p_k$ that ${(p_k-p_\ell)}/{p_\ell}>\theta$.
+Then, we mark that the span from $p_\ell$ to $p_k$ is an upward DC event, and the trend becomes upward.
+Similarly, if a market is in an uptrend, we keep updating the highest price $p_h$ in this uptrend until we find a price $p_k$ that ${(p_h-p_k)}/{p_h}>\theta$, then the ``$p_h$-to-$p_c$'' spans a downward DC event, and the trend becomes downward.
+After finishing looking through all daily Forex data, we obtain a series of DC events.
 
 \subsection{Interfaces and features}
-The interface of News Forexast can be divided into two main parts, a forex chart and the news section.
-Users can customize the selection criteria either by directly manipulating the forex chart or applying the keyword filters.
+The interface of INForex can be divided into two main parts: 1) a Forex chart (in the left panel of the system) and 2) the news section (in the right panel of the system).
+Users are allowed to customize the selection criteria either by directly manipulating the Forex chart or applying the keyword filters.
 
@@
   \caption{Example of news being highlighted when the cursor hovers over the corresponding timeline on the chart. The yellow interval is the news selection range which can be decided by users.}
-  \Description{}
+  \label{fig:hover}
 \end{figure}
@@
 \subsubsection{Interactive Forex Chart}
-The forex chart is a standard candlestick chart, powered by Plotly graphing libraries\footnote{\url{https://https://plotly.com/graphing-libraries/}}, that displays price movements, users can specify the date they are interested in with the calendar icon above the chart.
-Supported by Plotly graphing library, users can explore the chart freely by zooming in or dragging out the time frame they are interested.
-The corresponding news would be highlighted if users hover over the corresponding blue line on the chart.
-(Fig.
-2)
-
-Below the calendar is where users can specify event types and the corresponding thresholds.
-After selecting an event type and their thresholds, eg.
-SD and low threshold,  the algorithmic output would be shown on the forex chart.
-Once done with a specific setting, users can clear the setting with the “clear all” button the top-right.
-The news section without any specification would show all daily news with titles, released time and sources.
-Users could link to the original posts and websites by clicking on the news cards.
+The Forex prices are displayed by a standard candlestick chart, powered by Plotly graphing libraries.\footnote{\url{https://https://plotly.com/graphing-libraries/}}
+Users can specify the date they are interested in with the calendar icon above the chart and then explore the chart freely by zooming in or dragging out the time frame they are interested.
+Except for the Forex chart, the blue vertical lines correspond the news releasing time points. 
+As shown in Figure~\ref{fig:hover}, the corresponding news in the right panel are highlighted if users hover over the corresponding blue line on the chart.
+Users can also link to the original posts and websites by clicking on the news cards.
+Moreover, users could easily spot specific time ranges they are interested in by double-clicking the start and end points of a period on the Forex chart (resulting in the yellow span in the figure); the news section in the right panel will change correspondingly according to the selected time span.
 
 \subsubsection{Forex Event Identifier}
-With the help of SD and DC events as indicators, users can now spot specific time ranges they are interested in.
-(Fig 3, 4) Users can then select such time range on the plot and narrow down the news shown on the right to the time range they selected.
-For example, users can specify 2019/08/30 with the SD with the low threshold, users can tell that there’s a dramatic change during 14:30-16:30 and can proceed to select the time range on the plot.
-In return, the news section would display related news such as "Would Warren Buffett Buy Greenland?" and "Risky Seller Financing Flourishes Where Homes Are Cheapest".
+Users can specify event types (i.e., SD or DC) and the corresponding thresholds (i.e., Low, Medium, or High) with the bottoms below the date selection calendar, after which the algorithm output would be shown on the Forex chart as the gray dots for the SD events and the span lines for the DC events (e.g., see Figures~\ref{fig:SD} and~\ref{fig:DC} for examples of SD and DC events, respectively).
+For example, users can specify August 30, 2019 and select the ``SD'' event with the ``Low'' threshold; from the upper panel of Figure~\ref{fig:SD}, users can tell that there exists a dramatic change during 14:30-16:30 on that day and can proceed to select a specific time range on the plot.
+In return, the news section would display related news such as ``Would Warren Buffett Buy Greenland?'' and ``Risky Seller Financing Flourishes Where Homes Are Cheapest.'' 
+Note that once done with a specific setting, users can clear the setting with the ``clear all'' button on the top-right of the left panel in the system; also, a higher threshold (the lower panels in Figures~\ref{fig:SD} and~\ref{fig:DC}) locates less events.
 
@@
   \includegraphics[width=\linewidth]{sd.png}
-  \caption{Examples of displaying SD events on 2019/08/30.
-The top is set to low threshold and the bottom is set to high threshold.
-Due to the higher sensitivity, almost all events of the latter are in the slump period around 16:00.}
+  \caption{Examples of displaying SD events on August 30, 2019. The upper panel is set to the ``Low'' threshold and the lower one is set to the ``High'' threshold.}
   \Description{}
+  \label{fig:SD}
 \end{figure}
@@
   \includegraphics[width=\linewidth]{dc.png}
-  \caption{Examples of displaying DC events on 2019/08/30.
-The top is set to low threshold and the bottom is set to high threshold.
-Due to the higher sensitivity, the latter only summarize the daily market into a downtrend and an uptrend.}
+  \caption{Examples of displaying DC events on August 30, 2019. The upper panel is set to ``Low'' threshold and the lower one is set to ``High'' threshold.}
   \Description{}
+  \label{fig:DC}
 \end{figure}
@@
 }
-If interested in more specific news, users can use the button under the plot to filter out news with selected keywords.
-We have placed several keywords such as U.S.
-and Trump, users can also customize their own tags by clicking the “+” button.
-For example, if the time frame is specified and the tag "U.S" is applied, only "Strength in U.S.
-Consumer Spending Drives Economy".
-would be shown on the news section.(Fig 5)
+If users are interested in more specific news, they can use the tags under the plot to filter out news with selected keywords.
+While we have placed several major keywords such as ``U.S.'' and ``Trump,'' as examples, users can customize their own tags by clicking the ``+'' button.
+Figure~\ref{fig:keywords} shows the displayed news based one different keyword and time filters.
 
@@
   \includegraphics[width=\linewidth]{news.png}
-  \caption{Examples of filtering news on 2019/08/30. From left to right are none, keyword: 'U.S.', time: '14:30-16:30', and both.}
+  \caption{Examples of filtering news on August 30, 2019. From left to right are none, keyword: ``U.S.,'' time: '14:30-16:30', and both.}
   \Description{}
+  \label{fig:keywords}
 \end{figure}
@@
   \Description{}
+  \label{fig:case}
 \end{figure}
 
-In this section, we provide an example that showcases the strong relation among events, news and forex (Fig 6).
-On 2019/08/06, we can see the news "Welcome to Turnaround Tuesday" released at 08:43, the time when an uptrend is about to end (displaying DC event with high threshold shows that this uptrend starts at 05:07).
-The news mentioned "U.S.
-stock futures were in a decidedly better mood as Tuesday began than on Monday." This indicates that U.S.
-stock is likely to rebound later, and thus causes appreciation on USD.
+In this section, we provide an example that showcases the strong relation among events, news and Forex in Figure~\ref{fig:case}.
+On August 6, 2019, we can see the news ``Welcome to Turnaround Tuesday'' released at 08:43, the time when an uptrend is about to end; note that the DC event with the High threshold shows that this uptrend starts at 05:07.
+The news mentioned ``U.S. stock futures were in a decidedly better mood as Tuesday began than on Monday,'' indicating that U.S. stock is likely to rebound later, and thus causes appreciation on USD.
 Then, the EUR/USD starts a downtrend from 08:49 to 14:41.
-Note that if EUR/USD has lower rate, it could be explained that USD has relatively high value.
+Note that if EUR/USD has a lower rate, it could be explained that USD has a relatively high value.
 
 \section{Conclusion and Future work}\label{sec:conclude}
-We have proposed an interactive website that juxtaposes a forex chart with news from the time frame users selecting.
-By having the chart and related news side by side together, users, financial professional or amateur investors, can all understand the trend quicker and easier.
-We are working toward to provide real-time news update in the future, as forex data is limited.
-In addition, if we are able to collect more user's log data and news in the future, along with machine learning and natural language processing (NLP) techniques, we can achieve more customized news feed such as personal news recommendation.
+In this paper, we propose an interactive system, INForex, that aligns the presentation of the Forex data and the textual news data in a unified and time-aware manner.
+By having the chart and related news side by side together, users, financial professionals, and amateur investors, can all understand the trend of Forex quicker and easier.
+Beyond the presentation in this paper, We are now working toward to provide real-time news update in the system.
+In addition, with the collected browsing behavior from users, we aim at providing more customized news feed via a personalized news recommender system by leveraging machine learning and natural language processing techniques.
 

### 2020-06-23 paper.tex
Submit to cikm 2020 demo -- cjwang.

--- 2020-06-14 paper.tex
@@
 \setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
+\copyrightyear{2020}
+\acmYear{2020}
 \acmDOI{10.1145/1122445.1122456}
@@
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Woodstock '18]{Woodstock '18: ACM Symposium on Neural
-  Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
-\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
-  June 03--05, 2018, Woodstock, NY}
+\acmConference[Online '20]{Online '20: 29th ACM International Conference on Information and Knowledge Management }{October 19--023, 2020}{Online}
+\acmBooktitle{ }
 \acmPrice{15.00}
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Forexast: A Interactive News Digestion for Forex Investors}
+% \title{INForex: An Interactive News Digestion for Forex Investors}
+  \title{INForex: Interactive News Digest for Forex Investors}   % AMH: check
 
@@
 %% used to denote shared contribution to the research.
-\author{Ben Trovato}
-\authornote{Both authors contributed equally to this research.}
-\email{trovato@corporation.com}
-\orcid{1234-5678-9012}
-\author{G.K.M. Tobin}
+
+\author{Yi-Shyuan Chiang}
+\authornote{These authors contributed equally to this work; author order was determined alphabetically.}
+\email{yschiang@gapp.nthu.edu.tw}
+\affiliation{%
+  \institution{Research Center for Information Technology Innovation, Academia Sinica}
+  \city{Taipei}
+  \country{Taiwan}}
+
+\author{Chih-Hen Lee}
 \authornotemark[1]
-\email{webmaster@marysville-ohio.com}
+\email{ch.lee@citi.sinica.edu.tw}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin}
-  \state{Ohio}
-  \postcode{43017-6221}
-}
+  \institution{Research Center for Information Technology Innovation, Academia Sinica}
+  \city{Taipei}
+  \country{Taiwan}}
 
-\author{Huifen Chan}
+\author{Chuan-Ju Wang}
+\email{cjwang@citi.sinica.edu.tw}
 \affiliation{%
-  \institution{Tsinghua University}
-  \streetaddress{30 Shuangqing Rd}
-  \city{Haidian Qu}
-  \state{Beijing Shi}
-  \country{China}}
-
-\author{Charles Palmer}
-\affiliation{%
-  \institution{Palmer Research Laboratories}
-  \streetaddress{8600 Datapoint Drive}
-  \city{San Antonio}
-  \state{Texas}
-  \postcode{78229}}
-\email{cpalmer@prl.com}
+  \institution{Research Center for Information Technology Innovation, Academia Sinica}
+  \city{Taipei}
+  \country{Taiwan}}
 
@@
 %% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+\renewcommand{\shortauthors}{Chiang, Lee, and Wang}
 
@@
 \begin{abstract}
-Foreign exchange (forex) markets reflect real-world events, local or global.
-Thus,  financial news is oftentimes referred to when making predicting the trends of forex.
-We propose News Forexast,  an interactive web-based system that displays a forex plot alongside with related financial news.
-Users can locate specific periods when the trading trends in forex markets dramatically change with the visualization of Standard Deviation (SD) events and Directional Change (DC) events.
-Finally, Forex comes with a keyword filtering function that allows users to filter news with keywords.
-We aim to make the decision-making process smoother for not only professional financial analysts but also all investors with this accessible and intuitive website.
+As foreign exchange (Forex) markets reflect real-world events, locally or
+globally,
+financial news is often leveraged to predict Forex trends.
+In this demonstration, we propose INForex, an interactive web-based system that
+displays a Forex plot alongside related financial news.
+To our best knowledge, this is the first system to successfully align the
+presentation of two types of time-series data---Forex data and textual
+news data---in a unified and time-aware manner. 
+Specifically, we first present two event detection methods based on the
+standard deviation (SD) and directional change (DC) of the Forex data and use
+these to locate specific periods during which prices or trends in Forex markets
+change dramatically.
+Moreover, INForex includes a keyword filtering function with which users can
+filter news with self-defined keywords.
+The system can be of great help in revealing valuable insight and relations
+between the two types of data and is thus valuable for decision making
+not only for professional financial analysts or traders but also for common
+investors.
+The system is available online at~\url{http://chlee.pythonanywhere.com/forex/}.
 \end{abstract}
@@
 \begin{teaserfigure}
-  \includegraphics[width=\textwidth]{teaser.png}
-  \caption{Forexast available at http://}
+  \includegraphics[width=\textwidth]{teaser.pdf}
+  \caption{INForex available at~\url{http://chlee.pythonanywhere.com/forex/}}
   \Description{}
@@
 \section{Introduction}
-Foreign exchange (Forex) market has been one of the most popular market for decades, with an estimated \$1\  trillion traded every day\cite{YAO200079}.
-Spot trading, options future and exchange-traded funds(ETFs) are three of many ways of investing strategies adopted in forex markets\cite{TradeForex}.
-The strategies might vary but they are driven by an intuitive rule of thumb, which is to buy low and sell high\cite{KOOLEN2014144}\cite{Zervos11}.
-Therefore, whether investors can accurately forecast the prices or trends is extremely crucial.
-Forex markets are influenced by numerous factors, such as producer price index(PPI), interest rates and politics, in order to consider as many factors as possible to have more comprehensive approaches for forex investment, investors rely on news for them to stay informed.
-Besides the fact that news usually reflect the real world events, the similar nature of news and forex also makes these two co-dependent.
-For example, if the Federal Reserve System (Fed) cuts the interest rate, it is more likely that the value of USD would drop, the devaluation would then feed into forex market increasing the demand, thus making another piece of news.
+The foreign exchange (Forex) market has been one of the most popular financial
+markets for decades, with an estimated \$1\ trillion traded every
+day~\cite{YAO200079}.
+Spot trading, currency options, currency futures, and currency exchange-traded
+funds (ETFs) are four major ways to trade Forex~\cite{TradeForex}.
+The strategies might vary but they are driven by an intuitive rule of thumb,
+which is to buy low and sell high~\cite{KOOLEN2014144,Zervos11}.
+Therefore, the crucial question is whether investors can accurately forecast 
+prices or trends.
 
-\section{Related Work and Systems}
-The dynamics between news and forex markets have been explored from several different aspects.
-Evans and Lyons proved that news can have significant effects on currency for days\cite{EVANS2005197}, and more specifically macro news can affect currency prices directly and indirectly via order flow\cite{EVANS200826}.
-There is also more evidence showcasing news and forex trend are correlated, Bauwens, Omrane and Giot show that volatility increases right before the announcement of scheduled news and unscheduled-but-periodic news\cite{BAUWENS20051108}, while Chatrath et al.
-suggests that prices respond quickly within 5-min of the news release\cite{CHATRATH201442}.
-With how forex markets and news interact in mind, it is only reasonable to suggest traders should begin their days by reading news commentary to determine the market sentiment and the daily direction for trading\cite{samuels2015trader}.
+Forex markets are influenced by numerous factors, including producer price index
+(PPI), interest rates, and politics.
+In order to consider as many factors as possible to gain a more comprehensive
+view for Forex investment, most investors stay informed by relying on news.
+Besides the fact that news usually reflects real-world events, the similar
+nature of news and Forex also makes these two co-dependent.
+For example, if the Federal Reserve System (the Fed) cuts the interest rate, it is
+more likely that the value of USD will drop; also, such a devaluation will
+later be the subject of another piece of news~\cite{"CNBC"}.
 
-There are many trading websites which provide useful information for forex investors, and each of them has its own features\cite{ForexWebsites}.
-For instance, BabyPips\cite{BabyPips} is a friendly website for junior traders, which provides not only forex plots and data but also courses, tutorials and forums for beginners.
-Bloomberg\cite{Bloomberg} is a well-known news agency.
-Therefore, besides stocks and currencies data, it also has various categories of news.
-TradingView\cite{TradingView} provides numerous functions in a page, such as watchlist, alerts, headlines and real-time chats, where users can customize the settings.
-However, some of their news and forex plot are not put in the same interface, or the times of news and forex are not highlighted.
-This could neglect the relation between news and forex data.
-Therefore, our work aims to highlight the connection between the timing of news and forex trends.
-New Forexast is designed to display the news’ release time as vertical lines on the forex plot to emphasize the order of breaking news and exchange rates.
-In addition, when users hover on the line, the background colour of the corresponding news would change.
-We also choose to display standard deviation events (SD events) and directional change events (DC events)\cite{7850020} to help users locate the changes within exchange rates, and pay more attention to the changes of trend or where the prices have larger volatility.
-The features of News Forexast would be introduced more detailed in section 4.
+Considering the critical role of news for Forex investment, in this
+demonstration, we propose INForex, an interactive web-based system that
+displays a Forex plot alongside related financial news.
+With the proposed system we seek to align the timing of Forex and news data 
+to highlight the connection between these two types of time-series data.
+In INForex the release time of news stories is displayed as vertical lines on the
+Forex plot to emphasize the order of breaking news and exchange rates. In
+addition, when users hover on a vertical line, the background color of the
+corresponding news changes. 
+Moreover, we propose using two event detection methods based on the standard
+deviation (SD) and directional change (DC)~\cite{7850020} of the Forex data to
+locate specific periods during which the prices or trends in Forex markets change dramatically.
+Via this design, we assist users by putting the focus on changes of trend or periods 
+of large price volatility.
+INForex also comes with a keyword filtering function that allows users to
+filter news with self-defined keywords.
+To our best knowledge, this is the first system that effectively visualizes these two
+types of time-series data---Forex data and textual news data---in a
+unified and time-aware manner. 
+The proposed INForex can be of great help in revealing valuable insight and
+relations between the two types of data and is thus valuable for
+decision-making not only for professional financial analysts or traders but
+also for common investors.
 
-\section{System Structure}
+The remainder of this paper is organized as follows.
+In Section~\ref{sec:related}, we review previous studies related to Forex and
+news and major websites for Forex traders.
+Section~\ref{sec:system} describes the proposed system with details related to
+data collection, event detection algorithms, interface, and key features.
+After that, we provide a case study in Section~\ref{sec:case}, and
+conclude and suggest future work in Section~\ref{sec:conclude}.
+
+\section{Related Work and Systems}\label{sec:related}
+The dynamics between news and Forex markets have been explored from several
+different aspects.
+Evans and Lyons~(2005) prove that news can have significant effects on currency
+for days~\cite{EVANS2005197}, and macro news can affect currency prices
+directly and indirectly via order flow~\cite{EVANS200826}.
+There is other evidence showing that news and Forex trend are correlated as well.
+For instance, Bauwens et al.~(2005) show that volatility increases right
+before the announcement of scheduled news and unscheduled-but-periodic
+news~\cite{BAUWENS20051108}, whereas Chatrath et al.~(2014) suggest that prices
+respond within a mere 5 minutes after the news release~\cite{CHATRATH201442}.
+Keeping in mind how Forex markets and news interact, it is reasonable for traders
+to begin their days by reading news commentary to determine the market
+sentiment and the direction for trading~\cite{samuels2015trader}.
+
+Apart from the literature discussing the relation between Forex and news, 
+many trading websites provide useful information for Forex investors,
+each of which has its own features and limitations~\cite{ForexWebsites}.
+For instance, BabyPips\footnote{\url{https://www.babypips.com}} is a friendly
+website for junior traders, providing not only Forex plots but also courses,
+tutorials, and forums for beginners.
+Bloomberg\footnote{\url{https://www.bloomberg.com}} is a well-known news
+agency; thus, in addition to currency data and plots, it also provides various
+categories of news for users to focus on.
+TradingView\footnote{\url{https://www.tradingview.com}} provides numerous
+functions in a page, including watchlist, alerts, headlines, and real-time chats,
+where users can customize the settings. 
+However, most of these websites do not put news and the Forex plot on the same
+page, or do not explicitly align the news release times with the Forex prices.
+Most neglect the time-dependent relation between news and Forex data
+and thus do not effectively visualize these two types of time-series data in a
+unified and time-aware manner.
+
+\section{System Description}\label{sec:system}
 
 \subsection{Data Collection}
-The forex data is from philipperemy/FX-1-Minute-Data\cite{FX-1-Minute-Data}, a repository of github.
-We choose the EUR/USD index, and use the DateTime Stamp, OPEN Bid Quote, HIGH Bid Quote, LOW Bid Quote and CLOSE Bid Quote columns as our forex data.
-The time span is from 2019/08/04 to 2019/09/13 except Saturdays, and the granularity of data is minute.
+The Forex data was collected from
+philipperemy/FX-1-Minute-Data.\footnote{\url{https://github.com/philipperemy/FX-1-Minute-Data}}
+For demonstration purposes, we chose the EUR/USD index and used the DateTime
+Stamp, OPEN Bid Quote, HIGH Bid Quote, LOW Bid Quote, and CLOSE Bid Quote
+columns to plot the Forex candlestick chart; moreover, the time span for the
+Forex data is from August 4, 2019 to September 13, 2019, and the granularity of
+data is minute. 
+As for news, we crawled articles from The Wall Street
+Journal,\footnote{\url{https://www.wsj.com}} each of which contains the title,
+the source, the release time, and the corresponding URL.
+In this demonstration, there are 1,116 articles in total.
 
-The news data is crawled by us, containing titles, sources, release times and urls. There are 1116 news in total and the sources are all from The Wall Street Journal\cite{WSJ}.
+\subsection{Event Detection Algorithms}\label{sec:algo}
+The proposed system comes with two event detection algorithms: one based on
+the standard deviation of Forex price differences (referred as SD events
+hereafter) and one based on the directional change of Forex prices (referred
+as DC events hereafter)~\cite{7850020}. 
+Specifically, SD events indicate time points during which the Forex prices
+dramatically change, whereas DC events show time points during which the trends of
+Forex prices change.
 
-\subsection{Algorithms for DC and SC events}
-To mark some special time points on the plot, we use two algorithms, standard deviation events (SD events) and directional change events (DC events)\cite{7850020}.
-SD events show the times where the prices dramatically change, and DC events show the times where the trends change.
-To get these events, we need to calculate the difference rate list $D$ of the price list first.
-Let $P= [p_1, p_2, ..., p_n]$, where $p_t$ stands for the CLOSE Bid Quote at minute $t$ and n equals to total numbers of daily forex data.
-Then we can get a difference rate list $D= [d_1, d_2, ..., d_m]$, where $d_t = \frac{p_{t+w}-p_t}{p_t}$.
-$w\in\mathbb Z^+$ means the range in minutes, which can be freely customized (we use 30 in this demonstration).
-$\sigma$ is the standard deviation of $D$, which can be interpreted as the volatility of prices.
-We use $\sigma$ as our low threshold to attain a subset of D, whose elements are all bigger than $\sigma$.
-Then the corresponding set of p will be marked as SD events.
-We also consider $2\sigma$ and $3\sigma$ as medium and high thresholds in our demonstration.
-Higher threshold will find less events.
+We here briefly describe the two algorithms.
+Let $P= [p_1, p_2, ..., p_n]$ denote a series of Forex prices, where $p_t$
+stands for the CLOSE Bid Quote at minute~$t$ and $n$ equals the total
+numbers of daily Forex data; also, the series of difference rates between two
+Forex prices is defined as $\mathcal{D}= [d_1, d_2, ..., d_m]$, where $d_t =
+{(p_{t+w}-p_t)}/{p_t}$ and $w\in\mathbb Z^+$ denotes the range in minutes.
+Note that we set $w=20$ in our prototype system.
+We first calculate the standard deviation of differences in list~$\mathcal{D}$
+and denote this as $\sigma_\mathcal{D}$; we then use the $z$-score of each
+difference to determine the events (i.e.,
+$z_{d_i}=(|d_i-m_{\mathcal{D}}|)/\sigma_{\mathcal{D}}>\tau$), where
+$m_{\mathcal{D}}$ denotes the mean of the list~$\mathcal{D}$.)
+In this demonstration, we consider $\tau=1,2,3$ as our thresholds 
+corresponding to labels \emph{Low}, \emph{Medium}, and \emph{High} in the
+system. 
+Note that a higher threshold locates fewer events.
 
-Under the DC framework, the market is summarized into alternating uptrends and downtrends\cite{7850020}.
-A DC event, including a start point and an end point, can be seen as a period that the trend starts to change.
-At first, we do not know the prices start with a upward or downward trend, so we let the first element of price $p_1$ as a base.
-Then we start looking through the list until we find a current price $p_c$, where $|\frac{p_c-p_1}{p_1}| > \theta$, $\theta$ can be set to $\sigma$, $2\sigma$, $3\sigma$ as above mentioned.
-If $p_c > p_1$, that means the span from $p_1$ to $p_c$ is an upward DC event; otherwise, it is a downward DC event.
-After finding the first DC event, we still have to look through the rest.
-Let us consider a market starts with a downtrend, which means we are now in an downtrend and waiting for a next uptrend.
-We keep updating the lowest price $p_l$ in this downtrend until we find a current price $p_c$ that $\frac{p_c-p_l}{p_l} > \theta$.
-Then, we mark that the span from $p_l$ to $p_c$ is a upward DC event, and the trend become upward.
-Similarly, if a market is in a uptrend, we keep updating the highest price $p_h$ until we find a current $p_c$ that $\frac{p_h-p_c}{p_c} > \theta$, then $p_h$ to $p_c$ is a downward DC event, and the trend become downward.
-After finishing looking through all daily forex data, we can get a series of alternating DC events.
+As for the DC events, the market is summarized into a set of uptrend and
+downtrend events~\cite{7850020}.
+A DC event, which includes a start point and an end point, can be seen as a period
+during which the trend starts to change.
+Initially, we use the first element in the price list~$p_1$ as the starting point
+of the algorithm; then, the algorithm starts looking through the price list~$P$
+in a sequential manner until it locates a price~$p_c$ for which
+$|{(p_c-p_1)}/{p_1}|>\theta$.
+In this demonstration, we consider
+$\theta=\sigma_{\mathcal{D}},2\sigma_{\mathcal{D}},3\sigma_{\mathcal{D}}$ as
+our thresholds, corresponding to labels \emph{Low},
+\emph{Medium}, and \emph{High} in the system.
+If $p_c > p_1$, the span from $p_1$ to $p_c$ denotes an upward DC event;
+otherwise, it is a downward DC event.
+After finding the first DC event, we look for other DC events in the
+rest of the price sequence.
+Let us consider a market starting with a downtrend, meaning that the Forex market
+is now in a downtrend and waiting for a next uptrend: we continue
+updating the lowest price $p_\ell$ in this downtrend until we find a 
+price~$p_k$ for which ${(p_k-p_\ell)}/{p_\ell}>\theta$. Then, we note that the span from
+$p_\ell$ to $p_k$ is an upward DC event, and the trend becomes an upward one.
+Similarly, if a market is in an uptrend, we continue to update the highest 
+price~$p_h$ in this uptrend until we find a price~$p_k$ for which
+${(p_h-p_k)}/{p_h}>\theta$, in which case the ``$p_h$-to-$p_c$'' spans a downward DC
+event, and the trend becomes a downward one.
+After finishing examining all the daily Forex data, we have a series of DC events.
 
-\section{Interfaces and features}
-The interface of News Forexast can be divided into two main parts, a forex chart and the news section.
-Users can customize the selection criteria either by directly manipulating the forex chart or applying the keyword filters.
+\subsection{Interfaces and features}
+The INForex interface can be divided into two main parts: 1) the Forex chart
+(in the left panel of the system) and 2) the news section (the right panel).
+Users customize the selection criteria either by directly
+manipulating the Forex chart or applying keyword filters.
 
@@
   \centering
-  \includegraphics[width=\linewidth]{hover.png}
-  \caption{Example of news being highlighted when the cursor hovers over the corresponding timeline on the chart.}
-  \Description{}
+  \includegraphics[width=\linewidth]{hover.pdf}
+  \caption{The interfaces of INForex. Note that news is highlighted when the cursor hovers over the
+  corresponding timeline on the chart. The yellow interval is the news
+  selection range which can be decided by users.}
+  \label{fig:hover}
 \end{figure}
 
-\subsection{Interactive Forex Chart}
-The forex chart is a standard candlestick chart, powered by Plotly graphing libraries\cite{Plotly}, that displays price movements, users can specify the date they are interested in with the calendar icon above the chart.
-Supported by Plotly graphing library, users can explore the chart freely by zooming in or dragging out the time frame they are interested.
-The corresponding news would be highlighted if users hover over the corresponding blue line on the chart.
-(Fig.
-2)
+\subsubsection{Interactive Forex Chart}
+Forex prices are displayed by a standard candlestick chart, powered by
+Plotly graphing
+libraries.\footnote{\url{https://https://plotly.com/graphing-libraries/}}
+Users specify the date they are interested in with the calendar icon above
+the chart and then explore the chart freely by zooming in or dragging out the
+time frame of interest.
+Except for the Forex chart, the blue vertical lines correspond to the news story
+release time points. 
+As shown in Figure~\ref{fig:hover}, the corresponding news in the right panel
+is highlighted if users hover over the corresponding blue line on the chart.
+Users also link to the original posts and websites by clicking on the news
+cards.
+Moreover, users can easily spot specific time ranges of interest
+by single-clicking the start and end points of a period on the Forex chart
+(resulting in the yellow span in the figure); the news section in the right
+panel changes correspondingly according to the selected time span.
 
-Below the calendar is where users can specify event types and the corresponding thresholds.
-After selecting an event type and their thresholds, eg.
-SD and low threshold,  the algorithmic output would be shown on the forex chart.
-Once done with a specific setting, users can clear the setting with the “clear all” button the top-right.
-The news section without any specification would show all daily news with titles, released time and sources.
-Users could link to the original posts and websites by clicking on the news cards.
-
-\subsection{Forex Event Identifier}
-With the help of SD and DC events as indicators, users can now spot specific time ranges they are interested in.
-(Fig 3, 4) Users can then select such time range on the plot and narrow down the news shown on the right to the time range they selected.
-For example, users can specify 2019/08/30 with the SD with the low threshold, users can tell that there’s a dramatic change during 14:30-16:30 and can proceed to select the time range on the plot.
-In return, the news section would display related news such as "Would Warren Buffett Buy Greenland?" and "Risky Seller Financing Flourishes Where Homes Are Cheapest".
+\subsubsection{Forex Event Identifier}
+Users specify event types (i.e., SD or DC)  and the corresponding thresholds (i.e., Low, Medium, or High) with the Forex event identifier (see the buttoms below the date selection calendar in Figure~\ref{fig:hover}), after which the algorithm output is shown on the Forex chart as
+gray dots for the SD events and span lines for the DC events (e.g., see
+Figures~\ref{fig:SD} and~\ref{fig:DC} for examples of SD and DC events,
+respectively).
+For example, users specify August 30, 2019 and select the ``SD'' event with
+the ``Low'' threshold; from the upper panel of Figure~\ref{fig:SD}, users 
+observe a dramatic change from 14:30 to 16:30 on this day (see the red box in the figure) and 
+proceed to select a specific time range on the plot. 
+In return, the news section displays related news such as ``Would Warren
+Buffett Buy Greenland?'' and ``Risky Seller Financing Flourishes Where Homes
+Are Cheapest''. 
+Note that once done with a specific setting, users clear the setting with
+the ``clear all'' button on the top-right of the left panel;
+a higher threshold (the lower panels in Figures~\ref{fig:SD}
+and~\ref{fig:DC}) locates fewer events.
 
@@
   \centering
-  \includegraphics[width=\linewidth]{sd.png}
-  \caption{Examples of displaying SD events on 2019/08/30.
-The top is set to low threshold and the bottom is set to high threshold.
-Due to the higher sensitivity, almost all events of the latter are in the slump period around 16:00.}
+  \includegraphics[width=\linewidth]{sd.pdf}
+  \caption{Display of SD events on August 30, 2019. The upper panel
+  is set to the ``Low'' threshold and the lower one is set to the ``High''
+  threshold.}
   \Description{}
+  \label{fig:SD}
 \end{figure}
@@
   \centering
-  \includegraphics[width=\linewidth]{dc.png}
-  \caption{Examples of displaying DC events on 2019/08/30.
-The top is set to low threshold and the bottom is set to high threshold.
-Due to the higher sensitivity, the latter only summarize the daily market into a downtrend and an uptrend.}
+  \includegraphics[width=\linewidth]{dc.pdf}
+  \caption{Display of DC events on August 30, 2019. Upper panel
+  set to ``Low'', lower panel to ``High''.}
   \Description{}
+  \label{fig:DC}
 \end{figure}
 
-\subsection{Customizable Keyword Filter
+\subsubsection{Customizable Keyword Filter
 }
-If interested in more specific news, users can use the button under the plot to filter out news with selected keywords.
-We have placed several keywords such as U.S.
-and Trump, users can also customize their own tags by clicking the “+” button.
-For example, if the time frame is specified and the tag "U.S" is applied, only "Strength in U.S.
-Consumer Spending Drives Economy".
-would be shown on the news section.(Fig 5)
+If users are interested in more specific news, they use the tags under the
+plot to filter out news with selected keywords.
+As examples, we have placed several major keywords such as ``U.S.'' and ``Trump'';
+users customize their own tags by clicking the ``+'' button.
+Figure~\ref{fig:keywords} shows the displayed news based on different keywords
+and time filters.
 
@@
   \centering
-  \includegraphics[width=\linewidth]{news.png}
-  \caption{Examples of filtering news on 2019/08/30. From left to right are none, keyword: 'U.S.', time: '14:30-16:30', and both.}
+  \includegraphics[width=\linewidth]{news.pdf}
+  \caption{Filtering news on August 30, 2019. From left to right
+  are none, keyword: ``U.S.'', time: `14:30--16:30', and both.}
   \Description{}
+  \label{fig:keywords}
 \end{figure}
 
-\section{Conclusion and Future work}
-We have proposed an interactive website that juxtaposes a forex chart with news within the time frame users selecting.
-By having the chart and related news side by side together, users, financial professional or amateur investors, can all understand the trend quicker and easier.
-We are working toward to provide real-time news update in the future, as fixed data is limited.
-In addition, if we are able to collect more user's log data and news in the future, along with machine learning and natural language processing (NLP) techniques, we can achieve more customized news feed such as personal news recommendation.
+\section{Case Study}\label{sec:case}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\linewidth]{case.pdf}
+  \caption{Case study}
+  \Description{}
+  \label{fig:case}
+\end{figure}
+
+In this section, we provide an example to show the strong relation among
+events, news, and Forex, as shown in Figure~\ref{fig:case}.
+On August 6, 2019, we see that the ``Welcome to Turnaround Tuesday''
+article released at 08:43, the time when an uptrend is about to end; note that the DC
+event with the High threshold shows that this uptrend starts at 05:07.
+The news mentions ``U.S. stock futures were in a decidedly better mood as
+Tuesday began than on Monday'', indicating that U.S. stock is likely to rebound
+later, thus causing appreciation on USD.
+Then, the EUR/USD starts a downtrend from 08:49 to 14:41.
+Note lower rates for EUR/USD could be due to a relatively high value for USD.
+
+\section{Conclusion and Future work}\label{sec:conclude}
+In this paper, we propose INForex, an interactive system that aligns the
+presentation of Forex data and textual news data in a unified and
+time-aware manner.
+By placing the chart and related news side by side, users, financial
+professionals, and amateur investors all understand Forex trends
+quicker and easier.
+Beyond the presentation in this paper, we are now working toward providing
+real-time news updates in the system.
+In addition, with the collected browsing behavior from users, we hope to
+provide more customized news feed via a personalized news recommender system
+by leveraging machine learning and natural language processing techniques.
 
 \section{Acknowledgments}
+We thank Po-Chuan Chien for collecting the news articles and Chen-Hung Pai for providing valuable comments regarding the design of the proposed system.
+This project was supported in part by the Ministry of Science and Technology in Taiwan under the grants MOST 108-2218-E-009-049.
 

### 2021-12-24 samplepaper.tex
Submitted to ECIR 2022 Demo -- CH

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{bbm}
\urlstyle{same}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{INForex: Interactive News Digest for Forex Investors}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Chih-Hen Lee\inst{1}\and
Yi-Shyuan Chiang\inst{2} \and
Chuan-Ju Wang\inst{3}}
%
\authorrunning{Lee et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Research Center for Information Technology Innovation, \\Academia Sinica, Taipei, Taiwan\\
\email{\{\inst{1}ch.lee, \inst{3}cjwang\}@citi.sinica.edu.tw} \\
\email{\inst{2}yschiang@gapp.nthu.edu.tw}
\\}
%
\maketitle              % typeset the header of the contribution
%
\vspace{-0.6cm}
\begin{abstract}
As foreign exchange (Forex) markets reflect real-world events, locally or globally, financial news is often leveraged to predict Forex trends. 
In this demonstration, we propose INForex, an interactive web-based system that displays a Forex plot alongside related financial news. To our best knowledge, this is the first system to successfully align the presentation of two types of time-series data---Forex data and textual news data---in a unified and time-aware manner and as well as the first Forex-related online system leveraging deep learning techniques. 
The system can be of great help in revealing valuable insights and relations between the two types of data and is thus valuable for decision making not only for professional financial analysts or traders but also for common investors.
The system is available online at~\url{http://chlee.pythonanywhere.com/forex/}, and the introduction video is at~\url{https://youtu.be/ZhFqQamTFY0}.

\keywords{FOREX  \and Attention Mechanism \and Web System.}
\end{abstract}
%
%
%
\vspace{-0.8cm}
\section{Introduction}
\vspace{-0.3cm}
Forex markets are influenced by numerous factors, including gross domestic product (GDP), interest rates, and politics.
In order to consider as many factors as possible to gain a more comprehensive view for Forex investment, most investors stay informed by relying on news.

Considering the critical role of news for Forex investment, in this demonstration, we propose INForex, an interactive web-based system that displays a Forex plot alongside related financial news. With the proposed system we seek to align the timing of Forex and news data to highlight the connection between these two types of time-series data. In INForex the release time of news stories is displayed as vertical lines on the Forex plot to emphasize the order of breaking news and exchange rates. Also, when users hover on a vertical line, the background color of the corresponding news will change.

Moreover, we propose using two event detection methods based on the standard deviation (SD) and directional change (DC)~\cite{7850020} of the Forex data to locate specific periods during which the prices or trends in Forex markets change dramatically.
Via this design, we assist users to make trading strategies by putting the focus on changes of trend or periods of large price volatility.
In addition, with the great advancement in natural language processing (NLP) and deep learning (DL) in recent years, in the proposed system, we utilize attention mechanisms~\cite{attention} to further exploit the semantics in financial news.
Specifically, by leveraging the financial news as training corpus and the aforementioned DC events as labels, our proposed system train an attention-based classification model that can be used to highlight worth-noting news and the potential keywords to users.
Last but not least, INForex also comes with a keyword filtering function that allows users to filter news with self-defined keywords, where they can focus on searching related news of their interests.

To our best knowledge, this is the first system that effectively visualizes these two types of time-series data---Forex data and textual news data---in a unified and time-aware manner and as well as the first Forex system leveraging deep learning techniques. 
The proposed INForex can be of great help in revealing valuable insight and relations between the two types of data and is thus valuable for decision-making not only for professional financial analysts or traders but also for common investors.

\vspace{-0.5cm}
\section{System Description}\label{sec:system}
\vspace{-0.9cm}
\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{hover.pdf}
  \caption{The interfaces of INForex. Note that news is highlighted when the cursor hovers over the
  corresponding timeline on the chart.}
  \label{fig:hover}
\end{figure}\
\vspace{-1.7cm}

\subsection{Data Collection}
\vspace{-0.3cm}
The Forex data was collected from
philipperemy/FX-1-Minute-Data.\footnote{\url{https://github.com/philipperemy/FX-1-Minute-Data}}
The training period is from January 1, 2010 to December 31, 2018, and the testing period is from August 4, 2019 to September 13, 2019 (which is the time span shown in the system).

As for news, we crawled articles from The Wall Street
Journal,\footnote{\url{https://www.wsj.com}}. Following the above setting, we separate these news into training, validation, and testing sets, the number of news corresponds to which are 80,000, 2,766, and 1,021, respectively
Note that the validation set is the last 2,766 news in the training period, and only the testing batch of news is displayed on our system.
\vspace{-0.5cm}
\subsection{Event Detection Algorithms}\label{sec:algo}
\vspace{-0.2cm}
The proposed system comes with two event detection algorithms: one based on
the standard deviation of Forex price differences (referred as SD events hereafter) and one based on the directional change of Forex prices (referred
as DC events hereafter)~\cite{7850020}. 
Specifically, SD events indicate time points during which the Forex prices
dramatically change, whereas DC events show time points where the trends of
Forex prices change.

We here briefly describe the two algorithms.
Let $P= [p_1, p_2, ..., p_n]$ denote a series of Forex prices, where $p_t$
stands for the CLOSE Bid Quote at minute~$t$ and $n$ equals the total
numbers of daily Forex data; also, the series of difference rates between two
Forex prices is defined as $\mathcal{D}= [d_1, d_2, ..., d_m]$, where $d_t =
{(p_{t+w}-p_t)}/{p_t}$ and $w\in\mathbbm{Z}^+$ denotes the range in minutes.
Note that we set $w=20$ in our prototype system.
We first calculate the standard deviation of differences in list~$\mathcal{D}$
and denote this as $\sigma_\mathcal{D}$; we then use the $z$-score of each
difference to determine the events (i.e.,
$z_{d_i}=(|d_i-m_{\mathcal{D}}|)/\sigma_{\mathcal{D}}>\tau$), where
$m_{\mathcal{D}}$ denotes the mean of the list~$\mathcal{D}$.)
In this demonstration, we consider $\tau=1,2,3$ as our thresholds 
corresponding to labels \emph{Low}, \emph{Medium}, and \emph{High} in the
system. 
Note that a higher threshold locates fewer events.

As for the DC events, the market is summarized into a set of uptrend and
downtrend events~\cite{7850020}.
A DC event, which includes a start point and an end point, can be seen as a period
during which the trend starts to change.
Initially, we use the first element in the price list~$p_1$ as the starting point; then, the algorithm starts looking through the price list~$P$
in a sequential manner until it locates a price~$p_c$ for which
$|{(p_c-p_1)}/{p_1}|>\theta$.
In this demo, we consider
$\theta=\sigma_{\mathcal{D}},2\sigma_{\mathcal{D}},3\sigma_{\mathcal{D}}$ as
our thresholds, corresponding to labels \emph{Low},
\emph{Medium}, and \emph{High} in the system.
If $p_c > p_1$, the span from $p_1$ to $p_c$ denotes an upward DC event;
otherwise, it is a downward DC event.
After finding the first DC event, we look for other DC events in the
rest of the price sequence.
\vspace{-0.5cm}
\subsection{Attention Model}
\vspace{-0.3cm}
In this subsection, we introduce the pipeline of our model in detail. First, we represent each word in news titles and content with the pre-trained embedding from GloVe.\footnote{\url{https://nlp.stanford.edu/projects/glove/}}
We later construct an attention layer~\cite{attention}
to aggregate the words embeddings in each news into one document embedding for each news.
According to~\cite{attention}, the attention mechanism is formulated as ${\rm Attention}(Q, K, V) = {\rm softmax}(QK\textsuperscript{T}/\sqrt{d_k})V$, where $d_k$ is the dimension of keys and queries. In our settings, the queries($Q$) are initially randomized, while the keys($K$) and values($V$) are the GloVe embeddings for words. Here, the main concept is that every word contributes to the document embeddings by different levels; therefore, if a word accounts for a much greater weight than other words in the document do, it might be a potential keyword. After getting the document embeddings, we first apply a ReLU activation function, and then pass the embeddings to a linear classification layer to predict the final label. In terms of labeling training data, a piece of news is labeled as positive when there is a start of any high-threshold DC event in the interval ${(t, t+30)}$, where $t$ is the news release time in minutes. Otherwise, it will be labeled as negative.

Other experimental details are listed as follows.
We implement the model under the PyTorch\footnote{\url{https://pytorch.org/}} framework. To reduce the training time, we only use the first 200 words in the concatenated news title and content as the textual input. For the training process, we select Adam~\cite{Adam} as the optimizer with learning rate 0.0001, and train data with 120 epochs and batch size 20.
\vspace{-0.5cm}
\subsection{Interfaces and features}
\vspace{-0.3cm}
The INForex interface can be divided into two main parts: 1) the Forex chart
(in the left panel of the system) and 2) the news section (the right panel).

\vspace{-0.2cm}
\subsubsection{Interactive Forex Chart}
\vspace{-0.2cm}
Forex prices are displayed by a standard candlestick chart, powered by
Plotly graphing
libraries.\footnote{\url{https://https://plotly.com/graphing-libraries/}}
Users can specify the date they are interested in with the calendar icon above
the chart and then explore the chart freely by zooming in or dragging out the
time frame of interest.
Except for the Forex chart, the blue vertical lines correspond to the news story
release time points. 
As shown in Figure~\ref{fig:hover}, the corresponding news in the right panel
is highlighted if users hover over the corresponding blue line on the chart.
Moreover, users can easily spot specific time ranges of interest
by single-clicking the start and end points of a period on the Forex chart
(resulting in the yellow span in the figure); the news section in the right
panel changes correspondingly according to the selected time span.

\vspace{-0.4cm}
\subsubsection{Forex Event Identifier}
\vspace{-0.2cm}
Users specify event types (i.e., SD or DC)  and the corresponding thresholds (i.e., Low, Medium, or High) with the Forex event identifier (see the buttoms below the date selection calendar in Figure~\ref{fig:hover}), after which the algorithm output is shown on the Forex chart as
gray dots for the SD events and span lines for the DC events.
Note that once done with a specific setting, users clear the setting with
the ``clear all'' button on the top-right of the left panel;
a higher threshold locates fewer events.

\subsubsection{Attention Weight Visualization}
\vspace{-1.3cm}
\begin{figure*}
  \centering
  \includegraphics[width=0.7\linewidth]{weights.pdf}
  \caption{Attention weights. The word ``clashes'' is a dark red word, ``pessimism'' and ``tariff'' are red words, and ``Beating'' and ``statisticians'' are pink words.}

  \label{fig:weights}
\end{figure*}
\vspace{-0.7cm}
If a news is predicted as positive (i.e., potentially highly correlated with the DC events), the news title is highlighted in red.
After clicking the positive news title, a window showcasing the news title and content with highlighted keywords will pop up.
Here, three classes of keywords are defined. Let $\ell$ be the word count of a concatenated news title and content, and the maximum of $\ell$ is set to 200 as mentioned above. The dark red words are the most worth-noting words whose attention weights are greater than ${40}/{\ell}$, while the attention weights of red words and pink words are greater than ${20}/{\ell}$ and ${10}/{\ell}$, respectively.
As shown in Figure~\ref{fig:weights}, our model is able to capture keywords related to the Forex market in this case.
\vspace{-0.5cm}
\section{Conclusion and Future Work}\label{sec:conclude}
\vspace{-0.3cm}
In this paper, we propose INForex, an interactive system that aligns the Forex data and textual news data in a unified and
time-aware manner.
By placing the chart and related news side by side and displaying the potential keywords, users, financial
professionals, and amateur investors can all understand Forex trends
quicker and easier.

With limited financial resources, we can only propose a static prototype system with data made available online. However, since the real-time feature is crucial for investors, we will thrive to make INForex become a real-time system in the future, either with real-time industrial APIs.
We hope that this demonstration can facilitate more research on predicting Forex markets through deep learning models in the future.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

\bibitem{7850020}
Amer Bakhach and Edward P. K. Tsang and Hamid Jalalian: Forecasting directional changes in the FX markets. In: Proceedings of the 2016 IEEE Symposium Series on Computational Intelligence (SSCI), pp. 1--8. (2010)

\bibitem{attention}
Vaswani, Ashish and Shazeer, Noam and Parmar, Niki and Uszkoreit, Jakob and Jones, Llion and Gomez, Aidan N and Kaiser, \L ukasz and Polosukhin, Illia: Attention is All you Need. In: Proceedings of the 31st International Conference on Neural Information Processing Systems (NeurIPS), pp. 6000--6010. (2017)

\bibitem{Adam}
Diederik P. Kingma and Jimmy Ba: Adam: A Method for Stochastic Optimization. In: Proceedings of the 3rd International Conference on Learning Representations (ICLR) (2015)

\end{thebibliography}
\end{document}

### 2022-01-05 paper.tex
Add makefiles, change url link, and rename files -- cjwang.

@@
-%%
-%% This is file `sample-sigconf.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `sigconf')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-sigconf.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf]{acmart}
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.20 of 2017/10/04
+%
+\documentclass[runningheads]{llncs}
+%
+\usepackage{times}
+\usepackage{soul}
+\usepackage{url}
+\usepackage[hidelinks]{hyperref}
+\usepackage[utf8]{inputenc}
+\usepackage[small]{caption}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{booktabs}
+\usepackage{bbm}
+\urlstyle{same}
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
+%
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
+% \renewcommand\UrlFont{\color{blue}\rmfamily}
 
-%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.
+\begin{document}
+%
+\title{INForex: Interactive News Digest for Forex Investors}
+%
+%\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{Chih-Hen Lee\inst{1}\and
+Yi-Shyuan Chiang\inst{2} \and
+Chuan-Ju Wang\inst{3}}
+%
+\authorrunning{Lee et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Research Center for Information Technology Innovation, \\Academia Sinica, Taipei, Taiwan\\
+\email{\{\inst{1}ch.lee, \inst{3}cjwang\}@citi.sinica.edu.tw} \\
+\email{\inst{2}yschiang@gapp.nthu.edu.tw}
+\\}
+%
+\maketitle              % typeset the header of the contribution
+%
+\vspace{-0.6cm}
+\begin{abstract}
+As foreign exchange (Forex) markets reflect real-world events, locally or globally, financial news is often leveraged to predict Forex trends. 
+In this demonstration, we propose INForex, an interactive web-based system that displays a Forex plot alongside related financial news.
+To our best knowledge, this is the first system to successfully align the presentation of two types of time-series data---Forex data and textual news data---in a unified and time-aware manner and as well as the first Forex-related online system leveraging deep learning techniques.
+The system can be of great help in revealing valuable insights and relations between the two types of data and is thus valuable for decision making not only for professional financial analysts or traders but also for common investors.
+The system is available online at~\url{http://cfda.csie.org/forex/}, and the introduction video is at~\url{https://youtu.be/ZhFqQamTFY0}.
 
-%%%% As of May 2020, [sigchi] and [sigchi-a] are no longer used. Please use sigconf (above) for SIGCHI conferences.
+\keywords{FOREX  \and Attention Mechanism \and Web System.}
+\end{abstract}
+%
+%
+%
+\vspace{-0.8cm}
+\section{Introduction}
+\vspace{-0.3cm}
+Forex markets are influenced by numerous factors, including gross domestic product (GDP), interest rates, and politics.
+In order to consider as many factors as possible to gain a more comprehensive view for Forex investment, most investors stay informed by relying on news.
 
-%%%% Proceedings format for SIGPLAN conferences 
-% \documentclass[sigplan, anonymous, review]{acmart}
+Considering the critical role of news for Forex investment, in this demonstration, we propose INForex, an interactive web-based system that displays a Forex plot alongside related financial news.
+With the proposed system we seek to align the timing of Forex and news data to highlight the connection between these two types of time-series data.
+In INForex the release time of news stories is displayed as vertical lines on the Forex plot to emphasize the order of breaking news and exchange rates.
+Also, when users hover on a vertical line, the background color of the corresponding news will change.
 
-%%%% Proceedings format for conferences using one-column small layout
-% \documentclass[acmsmall,review]{acmart}
+Moreover, we propose using two event detection methods based on the standard deviation (SD) and directional change (DC)~\cite{7850020} of the Forex data to locate specific periods during which the prices or trends in Forex markets change dramatically.
+Via this design, we assist users to make trading strategies by putting the focus on changes of trend or periods of large price volatility.
+In addition, with the great advancement in natural language processing (NLP) and deep learning (DL) in recent years, in the proposed system, we utilize attention mechanisms~\cite{attention} to further exploit the semantics in financial news.
+Specifically, by leveraging the financial news as training corpus and the aforementioned DC events as labels, our proposed system train an attention-based classification model that can be used to highlight worth-noting news and the potential keywords to users.
+Last but not least, INForex also comes with a keyword filtering function that allows users to filter news with self-defined keywords, where they can focus on searching related news of their interests.
 
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
+To our best knowledge, this is the first system that effectively visualizes these two types of time-series data---Forex data and textual news data---in a unified and time-aware manner and as well as the first Forex system leveraging deep learning techniques.
+The proposed INForex can be of great help in revealing valuable insight and relations between the two types of data and is thus valuable for decision-making not only for professional financial analysts or traders but also for common investors.
 
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2020}
-\acmYear{2020}
-\acmDOI{10.1145/1122445.1122456}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[Online '20]{Online '20: 29th ACM International Conference on Information and Knowledge Management }{October 19--023, 2020}{Online}
-\acmBooktitle{ }
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
-%% end of the preamble, start of the body of the document source.
-\begin{document}
-
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
-% \title{INForex: An Interactive News Digestion for Forex Investors}
-  \title{INForex: Interactive News Digest for Forex Investors}   % AMH: check
-
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
-
-\author{Yi-Shyuan Chiang}
-\authornote{These authors contributed equally to this work; author order was determined alphabetically.}
-\email{yschiang@gapp.nthu.edu.tw}
-\affiliation{%
-  \institution{Research Center for Information Technology Innovation, Academia Sinica}
-  \city{Taipei}
-  \country{Taiwan}}
-
-\author{Chih-Hen Lee}
-\authornotemark[1]
-\email{ch.lee@citi.sinica.edu.tw}
-\affiliation{%
-  \institution{Research Center for Information Technology Innovation, Academia Sinica}
-  \city{Taipei}
-  \country{Taiwan}}
-
-\author{Chuan-Ju Wang}
-\email{cjwang@citi.sinica.edu.tw}
-\affiliation{%
-  \institution{Research Center for Information Technology Innovation, Academia Sinica}
-  \city{Taipei}
-  \country{Taiwan}}
-
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-\renewcommand{\shortauthors}{Chiang, Lee, and Wang}
-
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
-\begin{abstract}
-As foreign exchange (Forex) markets reflect real-world events, locally or
-globally,
-financial news is often leveraged to predict Forex trends.
-In this demonstration, we propose INForex, an interactive web-based system that
-displays a Forex plot alongside related financial news.
-To our best knowledge, this is the first system to successfully align the
-presentation of two types of time-series data---Forex data and textual
-news data---in a unified and time-aware manner. 
-Specifically, we first present two event detection methods based on the
-standard deviation (SD) and directional change (DC) of the Forex data and use
-these to locate specific periods during which prices or trends in Forex markets
-change dramatically.
-Moreover, INForex includes a keyword filtering function with which users can
-filter news with self-defined keywords.
-The system can be of great help in revealing valuable insight and relations
-between the two types of data and is thus valuable for decision making
-not only for professional financial analysts or traders but also for common
-investors.
-The system is available online at~\url{http://chlee.pythonanywhere.com/forex/}.
-\end{abstract}
-
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-\begin{CCSXML}
-<ccs2012>
-   <concept>
-       <concept_id>10002951.10003260.10003282</concept_id>
-       <concept_desc>Information systems~Web applications</concept_desc>
-       <concept_significance>500</concept_significance>
-       </concept>
- </ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Information systems~Web applications}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{Forex, financial news, standard deviation, directional change}
-
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-\begin{teaserfigure}
-  \includegraphics[width=\textwidth]{teaser.pdf}
-  \caption{INForex available at~\url{http://chlee.pythonanywhere.com/forex/}}
-  \Description{}
-  \label{fig:teaser}
-\end{teaserfigure}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
-
-\section{Introduction}
-The foreign exchange (Forex) market has been one of the most popular financial
-markets for decades, with an estimated \$1\ trillion traded every
-day~\cite{YAO200079}.
-Spot trading, currency options, currency futures, and currency exchange-traded
-funds (ETFs) are four major ways to trade Forex~\cite{TradeForex}.
-The strategies might vary but they are driven by an intuitive rule of thumb,
-which is to buy low and sell high~\cite{KOOLEN2014144,Zervos11}.
-Therefore, the crucial question is whether investors can accurately forecast 
-prices or trends.
-
-Forex markets are influenced by numerous factors, including producer price index
-(PPI), interest rates, and politics.
-In order to consider as many factors as possible to gain a more comprehensive
-view for Forex investment, most investors stay informed by relying on news.
-Besides the fact that news usually reflects real-world events, the similar
-nature of news and Forex also makes these two co-dependent.
-For example, if the Federal Reserve System (the Fed) cuts the interest rate, it is
-more likely that the value of USD will drop; also, such a devaluation will
-later be the subject of another piece of news~\cite{"CNBC"}.
-
-Considering the critical role of news for Forex investment, in this
-demonstration, we propose INForex, an interactive web-based system that
-displays a Forex plot alongside related financial news.
-With the proposed system we seek to align the timing of Forex and news data 
-to highlight the connection between these two types of time-series data.
-In INForex the release time of news stories is displayed as vertical lines on the
-Forex plot to emphasize the order of breaking news and exchange rates. In
-addition, when users hover on a vertical line, the background color of the
-corresponding news changes. 
-Moreover, we propose using two event detection methods based on the standard
-deviation (SD) and directional change (DC)~\cite{7850020} of the Forex data to
-locate specific periods during which the prices or trends in Forex markets change dramatically.
-Via this design, we assist users by putting the focus on changes of trend or periods 
-of large price volatility.
-INForex also comes with a keyword filtering function that allows users to
-filter news with self-defined keywords.
-To our best knowledge, this is the first system that effectively visualizes these two
-types of time-series data---Forex data and textual news data---in a
-unified and time-aware manner. 
-The proposed INForex can be of great help in revealing valuable insight and
-relations between the two types of data and is thus valuable for
-decision-making not only for professional financial analysts or traders but
-also for common investors.
-
-The remainder of this paper is organized as follows.
-In Section~\ref{sec:related}, we review previous studies related to Forex and
-news and major websites for Forex traders.
-Section~\ref{sec:system} describes the proposed system with details related to
-data collection, event detection algorithms, interface, and key features.
-After that, we provide a case study in Section~\ref{sec:case}, and
-conclude and suggest future work in Section~\ref{sec:conclude}.
-
-\section{Related Work and Systems}\label{sec:related}
-The dynamics between news and Forex markets have been explored from several
-different aspects.
-Evans and Lyons~(2005) prove that news can have significant effects on currency
-for days~\cite{EVANS2005197}, and macro news can affect currency prices
-directly and indirectly via order flow~\cite{EVANS200826}.
-There is other evidence showing that news and Forex trend are correlated as well.
-For instance, Bauwens et al.~(2005) show that volatility increases right
-before the announcement of scheduled news and unscheduled-but-periodic
-news~\cite{BAUWENS20051108}, whereas Chatrath et al.~(2014) suggest that prices
-respond within a mere 5 minutes after the news release~\cite{CHATRATH201442}.
-Keeping in mind how Forex markets and news interact, it is reasonable for traders
-to begin their days by reading news commentary to determine the market
-sentiment and the direction for trading~\cite{samuels2015trader}.
-
-Apart from the literature discussing the relation between Forex and news, 
-many trading websites provide useful information for Forex investors,
-each of which has its own features and limitations~\cite{ForexWebsites}.
-For instance, BabyPips\footnote{\url{https://www.babypips.com}} is a friendly
-website for junior traders, providing not only Forex plots but also courses,
-tutorials, and forums for beginners.
-Bloomberg\footnote{\url{https://www.bloomberg.com}} is a well-known news
-agency; thus, in addition to currency data and plots, it also provides various
-categories of news for users to focus on.
-TradingView\footnote{\url{https://www.tradingview.com}} provides numerous
-functions in a page, including watchlist, alerts, headlines, and real-time chats,
-where users can customize the settings. 
-However, most of these websites do not put news and the Forex plot on the same
-page, or do not explicitly align the news release times with the Forex prices.
-Most neglect the time-dependent relation between news and Forex data
-and thus do not effectively visualize these two types of time-series data in a
-unified and time-aware manner.
-
+\vspace{-0.5cm}
 \section{System Description}\label{sec:system}
+\vspace{-0.9cm}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{hover.pdf}
+  \caption{The interfaces of INForex. Note that news is highlighted when the cursor hovers over the
+  corresponding timeline on the chart.}
+  \label{fig:hover}
+\end{figure}\
+\vspace{-1.7cm}
 
 \subsection{Data Collection}
+\vspace{-0.3cm}
 The Forex data was collected from
 philipperemy/FX-1-Minute-Data.\footnote{\url{https://github.com/philipperemy/FX-1-Minute-Data}}
-For demonstration purposes, we chose the EUR/USD index and used the DateTime
-Stamp, OPEN Bid Quote, HIGH Bid Quote, LOW Bid Quote, and CLOSE Bid Quote
-columns to plot the Forex candlestick chart; moreover, the time span for the
-Forex data is from August 4, 2019 to September 13, 2019, and the granularity of
-data is minute. 
+The training period is from January 1, 2010 to December 31, 2018, and the testing period is from August 4, 2019 to September 13, 2019 (which is the time span shown in the system).
+
 As for news, we crawled articles from The Wall Street
-Journal,\footnote{\url{https://www.wsj.com}} each of which contains the title,
-the source, the release time, and the corresponding URL.
-In this demonstration, there are 1,116 articles in total.
-
+Journal,\footnote{\url{https://www.wsj.com}}.
+Following the above setting, we separate these news into training, validation, and testing sets, the number of news corresponds to which are 80,000, 2,766, and 1,021, respectively
+Note that the validation set is the last 2,766 news in the training period, and only the testing batch of news is displayed on our system.
+\vspace{-0.5cm}
 \subsection{Event Detection Algorithms}\label{sec:algo}
+\vspace{-0.2cm}
 The proposed system comes with two event detection algorithms: one based on
-the standard deviation of Forex price differences (referred as SD events
-hereafter) and one based on the directional change of Forex prices (referred
+the standard deviation of Forex price differences (referred as SD events hereafter) and one based on the directional change of Forex prices (referred
 as DC events hereafter)~\cite{7850020}. 
 Specifically, SD events indicate time points during which the Forex prices
-dramatically change, whereas DC events show time points during which the trends of
+dramatically change, whereas DC events show time points where the trends of
 Forex prices change.
@@
 Forex prices is defined as $\mathcal{D}= [d_1, d_2, ..., d_m]$, where $d_t =
-{(p_{t+w}-p_t)}/{p_t}$ and $w\in\mathbb Z^+$ denotes the range in minutes.
+{(p_{t+w}-p_t)}/{p_t}$ and $w\in\mathbbm{Z}^+$ denotes the range in minutes.
 Note that we set $w=20$ in our prototype system.
@@
 during which the trend starts to change.
-Initially, we use the first element in the price list~$p_1$ as the starting point
-of the algorithm; then, the algorithm starts looking through the price list~$P$
+Initially, we use the first element in the price list~$p_1$ as the starting point; then, the algorithm starts looking through the price list~$P$
 in a sequential manner until it locates a price~$p_c$ for which
 $|{(p_c-p_1)}/{p_1}|>\theta$.
-In this demonstration, we consider
+In this demo, we consider
 $\theta=\sigma_{\mathcal{D}},2\sigma_{\mathcal{D}},3\sigma_{\mathcal{D}}$ as
@@
 rest of the price sequence.
-Let us consider a market starting with a downtrend, meaning that the Forex market
-is now in a downtrend and waiting for a next uptrend: we continue
-updating the lowest price $p_\ell$ in this downtrend until we find a 
-price~$p_k$ for which ${(p_k-p_\ell)}/{p_\ell}>\theta$. Then, we note that the span from
-$p_\ell$ to $p_k$ is an upward DC event, and the trend becomes an upward one.
-Similarly, if a market is in an uptrend, we continue to update the highest 
-price~$p_h$ in this uptrend until we find a price~$p_k$ for which
-${(p_h-p_k)}/{p_h}>\theta$, in which case the ``$p_h$-to-$p_c$'' spans a downward DC
-event, and the trend becomes a downward one.
-After finishing examining all the daily Forex data, we have a series of DC events.
+\vspace{-0.5cm}
+\subsection{Attention Model}
+\vspace{-0.3cm}
+In this subsection, we introduce the pipeline of our model in detail.
+First, we represent each word in news titles and content with the pre-trained embedding from GloVe.\footnote{\url{https://nlp.stanford.edu/projects/glove/}}
+We later construct an attention layer~\cite{attention}
+to aggregate the words embeddings in each news into one document embedding for each news.
+According to~\cite{attention}, the attention mechanism is formulated as ${\rm Attention}(Q, K, V) = {\rm softmax}(QK\textsuperscript{T}/\sqrt{d_k})V$, where $d_k$ is the dimension of keys and queries.
+In our settings, the queries($Q$) are initially randomized, while the keys($K$) and values($V$) are the GloVe embeddings for words.
+Here, the main concept is that every word contributes to the document embeddings by different levels; therefore, if a word accounts for a much greater weight than other words in the document do, it might be a potential keyword.
+After getting the document embeddings, we first apply a ReLU activation function, and then pass the embeddings to a linear classification layer to predict the final label.
+In terms of labeling training data, a piece of news is labeled as positive when there is a start of any high-threshold DC event in the interval ${(t, t+30)}$, where $t$ is the news release time in minutes.
+Otherwise, it will be labeled as negative.
 
+Other experimental details are listed as follows.
+We implement the model under the PyTorch\footnote{\url{https://pytorch.org/}} framework.
+To reduce the training time, we only use the first 200 words in the concatenated news title and content as the textual input.
+For the training process, we select Adam~\cite{Adam} as the optimizer with learning rate 0.0001, and train data with 120 epochs and batch size 20.
+\vspace{-0.5cm}
 \subsection{Interfaces and features}
+\vspace{-0.3cm}
 The INForex interface can be divided into two main parts: 1) the Forex chart
 (in the left panel of the system) and 2) the news section (the right panel).
-Users customize the selection criteria either by directly
-manipulating the Forex chart or applying keyword filters.
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{hover.pdf}
-  \caption{The interfaces of INForex. Note that news is highlighted when the cursor hovers over the
-  corresponding timeline on the chart. The yellow interval is the news
-  selection range which can be decided by users.}
-  \label{fig:hover}
-\end{figure}
-
+\vspace{-0.2cm}
 \subsubsection{Interactive Forex Chart}
+\vspace{-0.2cm}
 Forex prices are displayed by a standard candlestick chart, powered by
@@
 libraries.\footnote{\url{https://https://plotly.com/graphing-libraries/}}
-Users specify the date they are interested in with the calendar icon above
+Users can specify the date they are interested in with the calendar icon above
 the chart and then explore the chart freely by zooming in or dragging out the
@@
 is highlighted if users hover over the corresponding blue line on the chart.
-Users also link to the original posts and websites by clicking on the news
-cards.
 Moreover, users can easily spot specific time ranges of interest
@@
 
+\vspace{-0.4cm}
 \subsubsection{Forex Event Identifier}
+\vspace{-0.2cm}
 Users specify event types (i.e., SD or DC)  and the corresponding thresholds (i.e., Low, Medium, or High) with the Forex event identifier (see the buttoms below the date selection calendar in Figure~\ref{fig:hover}), after which the algorithm output is shown on the Forex chart as
-gray dots for the SD events and span lines for the DC events (e.g., see
-Figures~\ref{fig:SD} and~\ref{fig:DC} for examples of SD and DC events,
-respectively).
-For example, users specify August 30, 2019 and select the ``SD'' event with
-the ``Low'' threshold; from the upper panel of Figure~\ref{fig:SD}, users 
-observe a dramatic change from 14:30 to 16:30 on this day (see the red box in the figure) and 
-proceed to select a specific time range on the plot. 
-In return, the news section displays related news such as ``Would Warren
-Buffett Buy Greenland?'' and ``Risky Seller Financing Flourishes Where Homes
-Are Cheapest''. 
+gray dots for the SD events and span lines for the DC events.
 Note that once done with a specific setting, users clear the setting with
 the ``clear all'' button on the top-right of the left panel;
-a higher threshold (the lower panels in Figures~\ref{fig:SD}
-and~\ref{fig:DC}) locates fewer events.
+a higher threshold locates fewer events.
 
-\begin{figure}[h]
+\subsubsection{Attention Weight Visualization}
+\vspace{-1.3cm}
+\begin{figure*}
   \centering
-  \includegraphics[width=\linewidth]{sd.pdf}
-  \caption{Display of SD events on August 30, 2019. The upper panel
-  is set to the ``Low'' threshold and the lower one is set to the ``High''
-  threshold.}
-  \Description{}
-  \label{fig:SD}
-\end{figure}
+  \includegraphics[width=0.7\linewidth]{weights.pdf}
+  \caption{Attention weights. The word ``clashes'' is a dark red word, ``pessimism'' and ``tariff'' are red words, and ``Beating'' and ``statisticians'' are pink words.}
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{dc.pdf}
-  \caption{Display of DC events on August 30, 2019. Upper panel
-  set to ``Low'', lower panel to ``High''.}
-  \Description{}
-  \label{fig:DC}
-\end{figure}
+  \label{fig:weights}
+\end{figure*}
+\vspace{-0.7cm}
+If a news is predicted as positive (i.e., potentially highly correlated with the DC events), the news title is highlighted in red.
+After clicking the positive news title, a window showcasing the news title and content with highlighted keywords will pop up.
+Here, three classes of keywords are defined.
+Let $\ell$ be the word count of a concatenated news title and content, and the maximum of $\ell$ is set to 200 as mentioned above.
+The dark red words are the most worth-noting words whose attention weights are greater than ${40}/{\ell}$, while the attention weights of red words and pink words are greater than ${20}/{\ell}$ and ${10}/{\ell}$, respectively.
+As shown in Figure~\ref{fig:weights}, our model is able to capture keywords related to the Forex market in this case.
+\vspace{-0.5cm}
+\section{Conclusion and Future Work}\label{sec:conclude}
+\vspace{-0.3cm}
+In this paper, we propose INForex, an interactive system that aligns the Forex data and textual news data in a unified and
+time-aware manner.
+By placing the chart and related news side by side and displaying the potential keywords, users, financial
+professionals, and amateur investors can all understand Forex trends
+quicker and easier.
 
-\subsubsection{Customizable Keyword Filter
-}
-If users are interested in more specific news, they use the tags under the
-plot to filter out news with selected keywords.
-As examples, we have placed several major keywords such as ``U.S.'' and ``Trump'';
-users customize their own tags by clicking the ``+'' button.
-Figure~\ref{fig:keywords} shows the displayed news based on different keywords
-and time filters.
+With limited financial resources, we can only propose a static prototype system with data made available online.
+However, since the real-time feature is crucial for investors, we will thrive to make INForex become a real-time system in the future, either with real-time industrial APIs.
+We hope that this demonstration can facilitate more research on predicting Forex markets through deep learning models in the future.
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{news.pdf}
-  \caption{Filtering news on August 30, 2019. From left to right
-  are none, keyword: ``U.S.'', time: `14:30--16:30', and both.}
-  \Description{}
-  \label{fig:keywords}
-\end{figure}
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+% \bibliographystyle{splncs04}
+% \bibliography{mybibliography}
+%
+\begin{thebibliography}{8}
 
-\section{Case Study}\label{sec:case}
+\bibitem{7850020}
+Amer Bakhach and Edward P.
+K.
+Tsang and Hamid Jalalian: Forecasting directional changes in the FX markets.
+In: Proceedings of the 2016 IEEE Symposium Series on Computational Intelligence (SSCI), pp.
+1--8.
+(2010)
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\linewidth]{case.pdf}
-  \caption{Case study}
-  \Description{}
-  \label{fig:case}
-\end{figure}
+\bibitem{attention}
+Vaswani, Ashish and Shazeer, Noam and Parmar, Niki and Uszkoreit, Jakob and Jones, Llion and Gomez, Aidan N and Kaiser, \L ukasz and Polosukhin, Illia: Attention is All you Need.
+In: Proceedings of the 31st International Conference on Neural Information Processing Systems (NeurIPS), pp.
+6000--6010.
+(2017)
 
-In this section, we provide an example to show the strong relation among
-events, news, and Forex, as shown in Figure~\ref{fig:case}.
-On August 6, 2019, we see that the ``Welcome to Turnaround Tuesday''
-article released at 08:43, the time when an uptrend is about to end; note that the DC
-event with the High threshold shows that this uptrend starts at 05:07.
-The news mentions ``U.S. stock futures were in a decidedly better mood as
-Tuesday began than on Monday'', indicating that U.S. stock is likely to rebound
-later, thus causing appreciation on USD.
-Then, the EUR/USD starts a downtrend from 08:49 to 14:41.
-Note lower rates for EUR/USD could be due to a relatively high value for USD.
+\bibitem{Adam}
+Diederik P. Kingma and Jimmy Ba: Adam: A Method for Stochastic Optimization. In: Proceedings of the 3rd International Conference on Learning Representations (ICLR) (2015)
 
-\section{Conclusion and Future work}\label{sec:conclude}
-In this paper, we propose INForex, an interactive system that aligns the
-presentation of Forex data and textual news data in a unified and
-time-aware manner.
-By placing the chart and related news side by side, users, financial
-professionals, and amateur investors all understand Forex trends
-quicker and easier.
-Beyond the presentation in this paper, we are now working toward providing
-real-time news updates in the system.
-In addition, with the collected browsing behavior from users, we hope to
-provide more customized news feed via a personalized news recommender system
-by leveraging machine learning and natural language processing techniques.
-
-\section{Acknowledgments}
-We thank Po-Chuan Chien for collecting the news articles and Chen-Hung Pai for providing valuable comments regarding the design of the proposed system.
-This project was supported in part by the Ministry of Science and Technology in Taiwan under the grants MOST 108-2218-E-009-049.
-
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{reference}
-
+\end{thebibliography}
 \end{document}
-\endinput
-%%
-%% End of file `sample-sigconf.tex'.
